---
title: "Natural Ventilation Analysis Workflow"
# Author: Kazuki Horikoshi
# Date: 12/9/2024
# Description: Analyzing NV hours based on increased velocity
---
```{r}
# Public-facing analysis notebook
# Execution order:
# 1. Initialize config, helper sources, and canonical output paths
# 2. Optionally run local diagnostics / exploratory PMV checks
# 3. Build or reload cached metrics
# 4. Generate comfort-hours, poster, energy, heatmap, and CLO/MET outputs
```

# Reset the notebook environment before sourcing the analysis configuration.
rm(list = ls())

source("config.R")
source("src/io/availability_summary_io.R")
source("src/io/energy_io.R")
source("src/metrics/availability_metrics.R")
source("src/metrics/energy_metrics.R")
source("src/pipelines/availability_pipeline.R")
source("src/pipelines/energy_pipeline.R")
source("src/plots/plot_annotations.R")
source("src/plots/comfort_hours_plots.R")
source("src/plots/energy_plots.R")

# Phase 1: Canonical analysis output roots
initialize_canonical_output_dirs()

all_metrics_cache_path <- ensure_parent_dir(file.path(output_cache_dir, "all_metrics_bh_cache.rds"))
legacy_all_metrics_cache_path <- file.path(legacy_analysis_data_dir, "all_metrics_bh_cache.rds")

comfort_hours_output_root <- ensure_dir(output_comfort_hours_dir)
poster_output_root <- ensure_dir(output_poster_dir)

energy_matrix_output_csv <- ensure_parent_dir(file.path(output_energy_dir, "TotalSiteEnergy_AllCities.csv"))
energy_baseline_output_csv <- ensure_parent_dir(file.path(output_energy_dir, "TotalSiteEnergy_BaselineAllCities.csv"))
energy_figure_output_dir <- ensure_dir(output_energy_figures_dir)

heatmap_data_output_path <- ensure_parent_dir(file.path(output_heatmap_data_dir, "Heatmap_Data_All_Cities.RData"))
legacy_heatmap_data_output_path <- file.path(legacy_heatmap_data_dir, "Heatmap_Data_All_Cities.RData")
legacy_heatmap_backup_data_output_path <- file.path(legacy_heatmap_backup_data_dir, "Heatmap_Data_All_Cities.RData")
heatmap_afam_output_path <- ensure_parent_dir(file.path(output_heatmap_figures_dir, "CombinedHeatMap_AfAm.png"))
heatmap_aw_output_path <- ensure_parent_dir(file.path(output_heatmap_figures_dir, "CombinedHeatMap_Aw.png"))

clomet_output_dir <- ensure_dir(output_clomet_figures_dir)

## Optional Diagnostics and Exploratory Checks

```{r}
# Optional local diagnostics:
# - set show_setup_diagnostics <- TRUE in config.R to print the Python environment
# - set run_optional_input_check <- TRUE in config.R to inspect one PMV snapshot
```

if (show_setup_diagnostics) {
  py_config()
  display.brewer.all()
}

if (run_optional_input_check) {
  city_name <- diagnostic_city_name
  temp_range <- diagnostic_temp_range

  for (temp in temp_range) {
    file_name <- paste0("PMV_result_MaxOutdoor_", temp, ".RData")
    diagnostic_pmv_file_path <- file.path(pmv_snapshot_root, city_name, file_name)

    if (!file.exists(diagnostic_pmv_file_path)) {
      warning(paste("no file detected:", diagnostic_pmv_file_path))
      next
    }

    cat("\n==========================================================\n")
    cat("Checking:", file_name, "\n")
    cat("==========================================================\n\n")

    temp_env <- new.env()
    load(diagnostic_pmv_file_path, envir = temp_env)

    if (exists("all_pmv_data_for_case", envir = temp_env)) {
      main_list <- get("all_pmv_data_for_case", envir = temp_env)
    } else {
      warning(paste("object 'all_pmv_data_for_case' not found:", file_name))
      next
    }

    for (element_name in names(main_list)) {
      cat("-------------------------------------\n")
      cat("[Source] all_pmv_data_for_case\n")
      cat("[Element]", element_name, "\n")
      element_data <- main_list[[element_name]]
      str(element_data)
    }
  }
}

## Main Execution: Availability Metrics

```{r}
# Availability calculation for clo, met combination
```

# Availability metrics helpers: see src/metrics/availability_metrics.R
# Worker pipeline helper: see src/pipelines/availability_pipeline.R

# ==============================================================================
# 3. Main Execution Block (Nested Loops + Parallel)
# ==============================================================================

# --- Setup Cities ---
# Use city names from epw_dict unless a custom city vector is defined.
# all_cities <- c("Singapore", "Tokyo", ...) 
if (!exists("epw_dict")) stop("Please define 'epw_dict' or 'all_cities' vector first.")
all_cities <- names(epw_dict)
cities_to_run <- all_cities[21]

# --- Setup Parameters ---
target_max_outdoor_range <- 27:32
velocity_scenarios_for_metrics <- list(1.2, 1.6, NULL) 

cat("<<<<< ALL CITY METRICS CALCULATION START >>>>>\n")
cat("Target Cities:", length(cities_to_run), "\n")

# --- Start Cluster (Once) ---
num_cores <- parallel::detectCores() - 1
if (num_cores < 1) num_cores <- 1
cl <- makeCluster(num_cores)
registerDoSNOW(cl)
cat(paste("[Info] Parallel backend registered with", num_cores, "cores.\n"))

# --- Outer Loop: Cities ---
for (city in cities_to_run) {
  
  cat("\n\n##################################################\n")
  cat("###   STARTING METRICS ANALYSIS FOR:", city, "   ###\n")
  cat("##################################################\n")
  
  # --- Middle Loop: Velocity Scenarios ---
  for (max_v in velocity_scenarios_for_metrics) {
    
    vel_label <- if (is.null(max_v)) "2.0 (Original)" else as.character(max_v)
    cat(paste0("\n  [Info] Processing with max_velocity = ", vel_label, " m/s\n"))
    
    # Progress bar setup for the inner parallel loop
    pb <- txtProgressBar(max = length(target_max_outdoor_range), style = 3)
    progress <- function(n) setTxtProgressBar(pb, n)
    opts <- list(progress = progress)
    
    # --- Inner Loop (Parallel): Temperatures ---
    # foreach sends the exported helpers to each worker and runs one temperature case per task.
    results <- foreach(
      temp = target_max_outdoor_range, 
      .combine = c,
      .options.snow = opts,
      .packages = c("dplyr", "tidyr", "stringr"), 
      .export = c("filter_by_business_hours", 
                  "calculate_availability_optimized", 
                  "combine_availability_single", 
                  "calculate_violation_hours",
                  "process_single_case")
    ) %dopar% {
      
      # Run the worker task for one temperature case.
      process_single_case(
        max_outdoor = temp,
        country_name = city,
        max_velocity = max_v,
        start_hour = 9, 
        end_hour = 18, 
        tz = "UTC"
      )
      
    }
    
    close(pb) # close the progress bar
    # print(results)
  }
  
  cat(paste0("\n###   FINISHED ANALYSIS FOR:", city, "   ###\n"))
}

# --- Stop Cluster ---
stopCluster(cl)
cat("\n\n<<<<< ALL SELECTED CITIES PROCESSED. SCRIPT FINISHED. >>>>>\n")

## Main Execution: Cached Metrics and Summary Figures

```{r}
# Reload all metrics from saved availability metrics data for Business Hours *** No Need to Run when using graphs
```

# Reload all metrics from saved availability metrics data for Business Hours
# Availability summary I/O helper: see src/io/availability_summary_io.R

# Phase 2: move notebook save/load paths to analysis/output/
# --- Cached metrics reload ---
# Reuse the cached business-hour metrics when available.
cache_path <- all_metrics_cache_path
cache_load_path <- resolve_canonical_or_legacy_path(cache_path, legacy_all_metrics_cache_path)

# 1. Velocity scenarios to load
scenarios_to_load <- list(1.2, 1.6, NULL)

# --- 2. Load the cached data or rebuild from CSV summaries ---
if (file.exists(cache_load_path)) {
  # Cache hit: load the combined metrics directly.
  message("Cached data found! Loading from .rds...")
  all_metrics_bh <- readRDS(cache_load_path)

} else {
  # Cache miss: read the per-scenario CSV summaries and rebuild the cache.
  message("No cache found. Processing CSV files...")

  # Step 2: load each max_velocity scenario.
  all_metrics_list <- lapply(scenarios_to_load, function(v) {
    cat("Loading data for max_velocity scenario:", ifelse(is.null(v), "2.0 (original)", as.character(v)), "\n")
    load_all_metrics_summary_business_hours(
      epw_dict,
      27:32,
      start_hour = 9,
      end_hour = 18,
      max_velocity = v
    )
  })

  # Step 3: combine scenarios and add plotting metadata.
  all_metrics_bh <- dplyr::bind_rows(all_metrics_list) %>%
    add_violation_rate(window = "bh", start_hour = 9, end_hour = 18) %>%
    left_join(city_climate_mapping, by = "City")

  # Save the rebuilt cache for later runs.
  saveRDS(all_metrics_bh, cache_path)
  message("Processing complete. Data saved to cache for next time.")
}

# Quick preview of the loaded metrics.
head(all_metrics_bh)

```{r}
# Loading all datas to make graphs
```

# Re-load the cache explicitly before plotting.
all_metrics_bh <- readRDS(
  resolve_canonical_or_legacy_path(all_metrics_cache_path, legacy_all_metrics_cache_path)
)

# Quick preview of the cached metrics.
head(all_metrics_bh)
```{r}
# Comfortable hours + Hours increase
```
# ==============================================================================
# Helper function: Make a graph with increment
# ==============================================================================
# Comfort-hours plotting helper: see src/plots/comfort_hours_plots.R

# ==============================================================================
# Main execution (Modified for multiple velocity scenarios)
# ==============================================================================

# Define color palette
set2_colors <- brewer.pal(n = 3, name = "Set2")

# --- Define velocity scenarios to process ---
velocity_scenarios_to_plot <- c(1.2, 1.6, 2.0)

# --- Define desired city orders for consistent plotting ---
desired_order_afam <- c(
  # Af
  "Guam","Honiara","KualaLumpur","Singapore",
  # Am
  "Freetown","Jakarta","Lagos","Manila","Miami","SantoDomingo"
)
desired_order_aw <- c("Bangkok","Mumbai","Chennai","RioDeJaneiro","Darwin",
                      "Kolkata","Bengaluru","Hyderabad","Honolulu","Dhaka")


# --- Main loop over each velocity scenario ---
for (current_velocity in velocity_scenarios_to_plot) {

  cat(paste("\n\n======================================================\n"))
  cat(paste("--- Generating plots for Max Velocity:", current_velocity, "m/s ---\n"))
  cat(paste(W"======================================================\n"))

  # --- Create a specific, clear output directory for this velocity ---
  # e.g., "Comfort_Hours_Plots_v_max_1_2"
  velocity_dir_name <- paste0("Comfort_Hours_Plots_v_max_", gsub("\\.", "_", as.character(current_velocity)))
  output_dir_for_velocity <- file.path(comfort_hours_output_root, velocity_dir_name)

  # --- Filter the main data frame for the current velocity scenario ---
  metrics_for_velocity <- all_metrics_bh %>%
    dplyr::filter(MaxVelocity == current_velocity)

  # --- Plot for Af+Am group ---
  cat("\n--- Processing plot for plot group: Af+Am ---\n")
  grp_afam <- metrics_for_velocity %>%
    dplyr::filter(PlotGroup %in% c("Af","Am"))
    
  generate_increment_plot(
      group_data = grp_afam,
      current_plot_group = "Af+Am",
      output_dir = output_dir_for_velocity,
      max_v = current_velocity,
      city_order = desired_order_afam,
      city_display_mapping = city_display_mapping,
      city_climate_mapping = city_climate_mapping,
      set2_colors = set2_colors
    )
  
  # --- Plot for Aw group ---
  cat("\n--- Processing plot for plot group: Aw ---\n")
  grp_aw <- metrics_for_velocity %>%
    dplyr::filter(stringr::str_starts(PlotGroup, "Aw"))
    # dplyr::mutate(City = factor(City, levels = desired_order_aw))

  generate_increment_plot(
    group_data = grp_aw,
    current_plot_group = "Aw",
    output_dir = output_dir_for_velocity,
    max_v = current_velocity,
    city_order = desired_order_aw,
    city_display_mapping = city_display_mapping,
    city_climate_mapping = city_climate_mapping,
    set2_colors = set2_colors
  )
}

```{r}
# Poster plot: six selected cities with custom climate labels
```

# ==============================================================================
# Poster-specific execution for six selected cities
# ==============================================================================

poster_city_order <- c(
  "Singapore",
  "Lagos",
  "Manila",
  "Mumbai",
  "Hyderabad",
  "RioDeJaneiro"
)

poster_city_display_mapping <- tibble::tribble(
  ~City,            ~CityDisplay,
  "Singapore",      "Singapore",
  "Lagos",          "Lagos",
  "Mumbai",         "Mumbai",
  "Hyderabad",      "Hyderabad",
  "Manila",         "Manila",
  "RioDeJaneiro",   "Rio de Janeiro"
)

poster_city_climate_mapping <- tibble::tribble(
  ~City,            ~ClimateGroup,
  "Singapore",      "Af",
  "Lagos",          "Am",
  "Mumbai",         "Aw",
  "Hyderabad",      "Aw",
  "Manila",         "Am",
  "RioDeJaneiro",   "Aw"
)

poster_velocity_scenarios_to_plot <- c(2.0)

for (current_velocity in poster_velocity_scenarios_to_plot) {

  cat(paste("\n\n======================================================\n"))
  cat(paste("--- Generating poster plot for Max Velocity:", current_velocity, "m/s ---\n"))
  cat(paste("======================================================\n"))

  poster_velocity_dir_name <- paste0(
    "Poster6Cities_Comfort_Hours_Plots_v_max_",
    gsub("\\.", "_", as.character(current_velocity))
  )
  poster_output_dir_for_velocity <- file.path(
    poster_output_root,
    poster_velocity_dir_name
  )

  poster_metrics_for_velocity <- all_metrics_bh %>%
    dplyr::filter(
      MaxVelocity == current_velocity,
      City %in% poster_city_order
    )

  generate_increment_plot(
    group_data = poster_metrics_for_velocity,
    current_plot_group = "Poster6Cities",
    output_dir = poster_output_dir_for_velocity,
    max_v = current_velocity,
    city_order = poster_city_order,
    city_display_mapping = poster_city_display_mapping,
    city_climate_mapping = poster_city_climate_mapping,
    set2_colors = set2_colors,
    facet_ncol = 2,
    plot_width = 6.5,
    plot_height = 8.5,
    y_limits = c(0, 2500),
    y_breaks = c(0, 1000, 2000)
  )
}

```{r}
# Test - Comfort hour ratio
```
# Archived note:
# An older comfort-ratio test block was removed from the main notebook body during
# public cleanup because it was inactive and not part of the current workflow.


## Main Execution: Energy and Pareto Figures

```{r}
# Energy value
```
energy_plot_data <- prepare_energy_plot_data(
  epw_dict = epw_dict,
  all_metrics_bh = all_metrics_bh,
  main_temp_range = 27:32,
  baseline_temp_range = 22,
  base_path = simulation_csv_snapshot_root,
  main_output_csv = energy_matrix_output_csv,
  baseline_output_csv = energy_baseline_output_csv,
  kbtu_to_kwh = KBTU_TO_KWH,
  area_m2 = AREA_M2,
  city_display_mapping = city_display_mapping
)

```{r}
# Energy, violation plot
```

# =========================================================================
# PART 1: DATA PREPARATION
# =========================================================================

total_site_energy_df <- energy_plot_data$total_site_energy_df
total_site_energy_baseline_df <- energy_plot_data$total_site_energy_baseline_df
energy_long <- energy_plot_data$energy_long
energy_baseline_long <- energy_plot_data$energy_baseline_long
energy_processed <- energy_plot_data$energy_processed
violation_summary <- energy_plot_data$violation_summary
master_data <- energy_plot_data$master_data

# =========================================================================
# PART 2: PLOT CONFIGURATION
# =========================================================================

temperature_shapes <- c(16, 17, 15, 18, 8, 3)
energy_plot_palette <- RColorBrewer::brewer.pal(n = 8, name = "Set2")

# =========================================================================
# PART 3: EXECUTION & FINAL GRID ASSEMBLY
# =========================================================================

# Save the combined energy figures under the canonical analysis output folder.
output_dir <- energy_figure_output_dir

# --- Assemble and Save Energy Grid Plot ---
energy_panel_args <- list(
  palette = energy_plot_palette,
  temperature_shapes = temperature_shapes,
  x_breaks = seq(27, 32, by = 1),
  y_limits = c(60, 88),
  y_breaks = seq(60, 80, by = 10),
  inpanel_legend_args = list(
    x_range = c(27, 32),
    y_range = c(60, 88),
    n_per_row = 2,
    x_pad_left = 0.3,
    row_gap = 2.4,
    text_size = 3.5
  )
)

energy_grid_plot <- build_energy_grid_plot(
  master_data = master_data,
  plot_groups = plot_groups,
  panel_args = energy_panel_args
)

save_energy_plot(
  plot_obj = energy_grid_plot,
  output_path = file.path(output_dir, "0_energy_intensity_grid.png"),
  width = 7.5,
  height = 7,
  dpi = 300
)

# --- Assemble and Save Pareto Grid Plot ---
pareto_panel_args <- list(
  palette = energy_plot_palette,
  temperature_shapes = temperature_shapes,
  x_limits = c(0, 0.1),
  x_breaks = seq(0, 0.1, by = 0.02),
  y_limits = c(0, 0.45),
  y_breaks = seq(0, 0.4, by = 0.1),
  shape_legend_name = "Switch-over outdoor temperature (\u2103)",
  city_legend_args = list(
    y_start = 0.02,
    y_step = 0.032,
    x_seg_start = 0.063,
    x_seg_end = 0.068,
    x_text = 0.070,
    segment_linewidth = 1.5,
    text_size = 3.2
  )
)

pareto_grid_plot <- build_pareto_grid_plot(
  master_data = master_data,
  plot_groups = plot_groups,
  panel_args = pareto_panel_args
)

save_energy_plot(
  plot_obj = pareto_grid_plot,
  output_path = file.path(output_dir, "0_pareto_grid.png"),
  width = 7,
  height = 6.5,
  dpi = 300
)

## Main Execution: Heatmap Workflow

```{r}
# Day of time analysis - Optimal velocity map
```

# Data gathering for Optimal velocity

# 1. calculate data for heat map with temp and timeline
# -----------------------------------------------------
# Purpose:
#   Create averaged NV availability heatmap data by hour (only business hours),
#   for the given city and threshold.
# Notes:
#   - Business hours are [start_hour, end_hour) i.e., start inclusive, end exclusive.
#   - If you want to include 18:00 hour as well, pass end_hour = 19.

calculate_averaged_heatmap_data <- function(city_name, temp_threshold,
                                            pmv_comfort_threshold = 0.5,
                                            start_hour = 9, end_hour = 18) {
  
  cat("--- Calculating data for:", city_name, "with", temp_threshold, "\u2103 ---\n")

  base_data_path <- file.path(pmv_snapshot_root, city_name)
  pmv_rdata_file <- file.path(base_data_path, paste0("PMV_result_MaxOutdoor_", temp_threshold, ".RData"))
  csv_path <- file.path(
    simulation_csv_snapshot_root,
    city_name, paste0("MaxOutdoor_", temp_threshold), "model_updated.csv"
  )

  if (!file.exists(pmv_rdata_file) || !file.exists(csv_path)) return(NULL)

  load_env <- new.env()
  load(pmv_rdata_file, envir = load_env)
  all_pmv_data_for_case <- get("all_pmv_data_for_case", envir = load_env)

  # 1. Load the CSV timeline data.
  df_csv <- data.table::fread(csv_path, check.names = FALSE, data.table = FALSE)
  
  # Shift the CSV timestamps back by one hour to align with the PMV timeline.
  df_csv$datetime <- as.POSIXct(paste("2026", gsub("  ", " ", df_csv[[1]])), 
                                format="%Y %m/%d %H:%M:%S") - 3600
  df_csv <- df_csv[!is.na(df_csv$datetime), ]
  
  col_setpoint <- grep("Thermostat Cooling Setpoint Temperature", names(df_csv), value = TRUE)[1]
  df_csv$is_nv_active <- df_csv[[col_setpoint]] > (temp_threshold + 4.9)
  cooling_setpoint_df <- df_csv[, c("datetime", "is_nv_active")]

  # 2. Build hourly availability ratios for each MET/CLO combination.
  list_of_hourly_ratios <- lapply(names(all_pmv_data_for_case), function(combo_name) {
    PMV_list <- all_pmv_data_for_case[[combo_name]]

    avail_list_per_wind <- lapply(PMV_list, function(pmv_df) {
      # Shift PMV timestamps to match the CSV timeline.
      pmv_df$datetime <- as.POSIXct(pmv_df$datetime) - 3600
      
      df_merged <- merge(pmv_df, cooling_setpoint_df, by = "datetime")
      if (nrow(df_merged) == 0) return(NULL)

      df_merged$hour <- as.integer(format(df_merged$datetime, "%H"))
      df_merged <- df_merged[df_merged$hour >= start_hour & df_merged$hour < end_hour, ]

      pmv_cols <- grep("PMV_", names(df_merged), value = TRUE)
      avail_df <- df_merged %>%
        dplyr::mutate(dplyr::across(
          dplyr::all_of(pmv_cols),
          ~ ifelse(is_nv_active, as.integer(.x > -pmv_comfort_threshold & .x < pmv_comfort_threshold), 0),
          .names = "ava_{.col}"
        )) %>%
        dplyr::select(hour, dplyr::starts_with("ava_"))
      return(avail_df)
    })

    avail_list_per_wind <- avail_list_per_wind[!vapply(avail_list_per_wind, is.null, logical(1))]
    if (length(avail_list_per_wind) == 0) return(NULL)

    all_df <- do.call(rbind, avail_list_per_wind)
    num_days <- length(unique(format(df_csv$datetime, "%m/%d")))
    total_steps_per_hour_bin <- num_days * length(avail_list_per_wind)

    wind_cols <- grep("^ava_PMV_", names(all_df), value = TRUE)
    hourly_counts <- stats::aggregate(all_df[, wind_cols, drop = FALSE],
                                     by = list(Hour = all_df$hour), FUN = sum)

    return(hourly_counts %>% dplyr::mutate(dplyr::across(-Hour, ~ (.x / total_steps_per_hour_bin) * 100)))
  })

  # 3. Drop NULL scenarios before combining the hourly ratios.
  list_of_hourly_ratios <- list_of_hourly_ratios[!vapply(list_of_hourly_ratios, is.null, logical(1))]
  if (length(list_of_hourly_ratios) == 0) return(NULL)

  heatmap_data <- dplyr::bind_rows(list_of_hourly_ratios) %>%
    dplyr::group_by(Hour) %>%
    dplyr::summarise(dplyr::across(dplyr::everything(), ~ mean(.x, na.rm = TRUE)), .groups = "drop") %>%
    tidyr::pivot_longer(cols = -Hour, names_to = "wind_col_name", values_to = "availability_ratio") %>%
    dplyr::mutate(wind_speed_num = as.numeric(stringr::str_extract(wind_col_name, "[0-9.]+"))) %>%
    dplyr::filter(wind_speed_num %in% c(0.1, 0.4, 0.8, 1.2, 1.6, 2.0)) %>%
    dplyr::mutate(wind_speed = factor(wind_speed_num, levels = sort(unique(wind_speed_num), decreasing = TRUE))) %>%
    dplyr::select(Hour, wind_speed, availability_ratio)

  cat("  Success:", city_name, "\n")
  return(heatmap_data)
}

# --- 1) Set up the parallel heatmap calculation ---
# num_cores <- parallel::detectCores() - 1
num_cores <- 10

if (num_cores < 1) num_cores <- 1
cl <- makeCluster(num_cores)
registerDoSNOW(cl)

# Export required objects to each worker.
clusterExport(cl, c("calculate_averaged_heatmap_data", "city_temp_list"), envir = environment())

# --- 2) Run the parallel calculation ---
cat(paste0("\nStarting parallel calculation with ", num_cores, " cores...\n"))

# Progress bar setup
pb <- txtProgressBar(max = length(city_temp_list), style = 3)
progress <- function(n) setTxtProgressBar(pb, n)
opts <- list(progress = progress)

all_cities_heatmap_data_list <- foreach(
  city = names(city_temp_list),
  .packages = c("dplyr", "tidyr", "lubridate"),
  .options.snow = opts,
  .errorhandling = "pass"
) %dopar% {
  
  temp <- city_temp_list[[city]]
  res <- calculate_averaged_heatmap_data(city, temp, start_hour = 9, end_hour = 18)
  
  # Return one named list entry only when data was created.
  if (!is.null(res) && nrow(res) > 0) {
    return(setNames(list(res), city))
  } else {
    return(NULL)
  }
}

close(pb)
stopCluster(cl)

# --- 3) Combine the per-city results into one named list ---
# list(list(Guam = df), list(Tokyo = df)) -> list(Guam = df, Tokyo = df)
all_cities_heatmap_data <- do.call(c, all_cities_heatmap_data_list[!vapply(all_cities_heatmap_data_list, is.null, logical(1))])

# --- 4) Save the heatmap source data ---
save(all_cities_heatmap_data, file = heatmap_data_output_path)

message("\nAll data calculations finished. Data saved in 'all_cities_heatmap_data' object.")

```{r}
# Day of time figures - Optimal velocity map
```

# Load saved RData file
data_file <- resolve_canonical_or_legacy_path(
  heatmap_data_output_path,
  legacy_heatmap_data_output_path,
  additional_paths = legacy_heatmap_backup_data_output_path
)
if(file.exists(data_file)) {
  load(data_file)
} else {
  stop("Data file not found. Please run Part 1 first.")
}

# Group 2-column heatmap creation (facet version, legend 40%, color adjustment)
# -----------------------------------------------------
# Purpose:
#   Build a single facet heatmap per group set with 2 columns (half width each),
#   filter to business hours, cap legend at 40%, and save one image.
# Inputs:
#   - all_cities_heatmap_data: named list of DF per City (must include Hour, wind_speed, availability_ratio)
#   - city_climate_mapping: DF with at least columns City and ClimateGroup (and/or PlotGroup)
#   - target_cities: character vec of City names to include
#   - output_file: save path (.png)
#   - start_hour, end_hour: business hours (default 9-18 -> 9,10,...,17)
# Notes:
#   - Facet label shows "City\n(Temp\u2103)" when city_temp_df is provided
# -----------------------------------------------------

plot_group_heatmaps_two_columns <- function(all_cities_heatmap_data,
                                            city_climate_mapping,
                                            target_cities,
                                            output_file,
                                            city_temp_df = NULL,
                                            desired_order = NULL,
                                            start_hour = 9,
                                            end_hour = 18) {
  suppressPackageStartupMessages({
    library(dplyr)
    library(ggplot2)
    library(scales)
    library(RColorBrewer)
  })

  available <- intersect(target_cities, names(all_cities_heatmap_data))
  if (length(available) == 0) {
    message("No matching cities found. Skip.")
    return(invisible(NULL))
  }

  group_df <- bind_rows(all_cities_heatmap_data[available], .id = "City") %>%
    filter(Hour >= start_hour, Hour < end_hour) %>%
    left_join(city_climate_mapping %>% select(City, ClimateGroup), by = "City") %>%
    # --- Display name mapping (City -> CityDisplay) ---
    left_join(city_display_mapping, by = "City") %>%
    mutate(CityDisplay = coalesce(CityDisplay, City))

  # Label format: "CityDisplay (Af, 29\u2103)" (no line break)
  if (!is.null(city_temp_df)) {
    group_df <- left_join(group_df, city_temp_df, by = "City")
    group_df <- mutate(group_df, FacetLabel = paste0(CityDisplay, " (", ClimateGroup, ", ", Temp, "\u2103)"))
  } else {
    group_df <- mutate(group_df, FacetLabel = paste0(CityDisplay, " (", ClimateGroup, ")"))
  }

  # enforce desired order (desired_order is City keys, not display names)
  if (!is.null(desired_order)) {
    city_to_label <- group_df %>%
      distinct(City, FacetLabel) %>%
      mutate(City = as.character(City))

    ordered_levels <- city_to_label$FacetLabel[match(desired_order, city_to_label$City)]
    ordered_levels <- ordered_levels[!is.na(ordered_levels)]

    group_df$FacetLabel <- factor(group_df$FacetLabel, levels = unique(ordered_levels))
  }

  # --- color scale up to 40% ---
 set2_colors <- brewer.pal(8, "Set2")
  # Use the same green as "Comfortable Hours"
  comfort_green <- set2_colors[1]
  
  pal_cols <- c("grey95", comfort_green)
  pal_vals <- scales::rescale(c(0, 45))

#  pal_cols <- c("grey95", set2_colors[6], set2_colors[5])
#  pal_vals <- scales::rescale(c(0, 15, 40))

p <- ggplot(group_df, aes(x = Hour, y = wind_speed, fill = availability_ratio)) +
  geom_tile(color = "white", size = 0.2) +
  geom_text(aes(label = as.integer(round(availability_ratio, 0))), size = 3.2, color = "black") +
  facet_wrap(~ FacetLabel, ncol = 2, strip.position = "top") +
  scale_fill_gradientn(
    colors = pal_cols,
    values = pal_vals,
    limits = c(0, 45),
    breaks = seq(0, 40, 10),
    labels = function(x) paste0(x, "%"),
    name = "NV availability ratio"
  ) +
  scale_x_continuous(breaks = seq(start_hour, end_hour - 1, 1), expand = c(0, 0)) +
  labs(x = "Time of Day (Hour)", y = "Relative air speed (m/s)") +
  guides(
    fill = guide_colorbar(
      title.position = "left",        # title next to bar
      title.vjust = 0.5,              # vertically centered
      barheight = grid::unit(1.8, "mm"),
      barwidth  = grid::unit(55, "mm")
    )
  ) +
  theme_minimal(base_size = 12) +
  theme(
    # --- remove grids (keep clean heatmap) ---
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),

    # --- legend on top, compact spacing ---
    legend.position = "top",
    legend.direction = "horizontal",
    legend.box = "horizontal",
    legend.box.spacing = grid::unit(0, "pt"),
    legend.margin = margin(t = 0, r = 0, b = 0, l = 0),
    legend.title = element_text(margin = margin(r = 6)),  # space between title and bar
    legend.text  = element_text(margin = margin(t = 0)),

    # --- reduce wasted top whitespace ---
    plot.margin = margin(t = 2, r = 5, b = 5, l = 5),

    # --- facet strip styling (City label) ---
    strip.background = element_blank(),             # remove gray strip bg
    strip.text = element_text(size = 11, face = "bold"),
    strip.placement = "outside"
  )
#  <!-- fig_width <- 7 -->
#  <!-- fig_height <- max(2.0 * n_rows, 4) -->

  fig_width <- 7
  fig_height <- 8

  dir.create(dirname(output_file), recursive = TRUE, showWarnings = FALSE)
  ggsave(output_file, plot = p, width = fig_width, height = fig_height, dpi = 300, bg = "white")
  message("Saved: ", output_file)
}
# ---- End ----

# Build a lookup table for the city-specific target temperatures.
# Inputs:
# - all_cities_heatmap_data: list(City = df)
# - city_climate_mapping: DF with City, ClimateGroup (Af/Am/Aw), optionally PlotGroup
# - city_temp_list: named list or named numeric of optimal temps
# ---- End ----
# Convert city_temp_list to a data frame for facet labels.
city_temp_df <- data.frame(
  City = names(city_temp_list),
  Temp = unlist(city_temp_list),
  row.names = NULL
)

# Af + Am
plot_group_heatmaps_two_columns(
  all_cities_heatmap_data,
  city_climate_mapping,
  target_cities = desired_order_afam,
  output_file  = heatmap_afam_output_path,
  city_temp_df = city_temp_df,
  desired_order = desired_order_afam
)

# Aw
plot_group_heatmaps_two_columns(
  all_cities_heatmap_data,
  city_climate_mapping,
  target_cities = desired_order_aw,
  output_file  = heatmap_aw_output_path,
  city_temp_df = city_temp_df,
  desired_order = desired_order_aw
)
# ---- End ----


## Main Execution: CLO/MET Maps

```{r}
# Hours map for MET CLO combination
```

# hours_per_year ---------------------------------------------------------------
# Purpose: return the number of business-hour slots in one year.
hours_per_year <- function(start_hour = 9, end_hour = 18) {
  (end_hour - start_hour) * 365  # e.g. 9 hours/day * 365 = 3285
}
# ---- End ----

# 3. save directory
# -----------------------------------------------------
output_dir_base <- clomet_output_dir

# plot_clomet_maps_daytime (Af+Am / Aw only, with "City-Climate-Temp" labels)
## Purpose:
##   Generate daytime CLO/MET comfort maps for the Af+Am and Aw groups using the target temperature for each city.
##   - all_metrics_bh: daytime summary data with City, MaxOutdoorTemp, MET, CLO, ActualOKHours
##   - city_climate_mapping / optimal_temps: city metadata and target temperatures
##   - start_hour, end_hour: business-hour window used for the source metrics
##   - output_dir_base / num_cols_max: output location and max columns per combined figure
##   - contour_by / fill_max: contour interval and color-scale limit for comfort hours
##   - desired_order_afam: optional city order for Af+Am panels
##   - desired_order_aw: optional city order for Aw panels
##   - invisible list: group -> list(city = ggplot object)
## Dependencies:
##   dplyr, tibble, ggplot2, patchwork, akima, metR, scales, here
plot_clomet_maps_daytime <- function(
  all_metrics_bh,
  city_climate_mapping,
  optimal_temps,                  
  start_hour = 9, end_hour = 18,  
  output_dir_base = output_clomet_figures_dir,
  num_cols_max = 4,
  contour_by = 200,
  fill_max = 2500,
  # optional: enforce city order for Af+Am (vector of city names). leave NULL if not needed.
  desired_order_afam = NULL,
  desired_order_aw   = NULL
) {
  # ---- Build city -> TargetTemp table ----
  optimal_temps_df <- tibble::enframe(optimal_temps, name = "City", value = "TargetTemp")
  city_data <- dplyr::left_join(city_climate_mapping, optimal_temps_df, by = "City")
  
  if (!dir.exists(output_dir_base)) dir.create(output_dir_base, recursive = TRUE, showWarnings = FALSE)
  message("Starting comfort map generation for Af+Am and Aw (daytime)")
  
  # ---- Two combined groups only ----
  combined_groups <- list(
    "Af+Am" = c("Af","Am"),
    "Aw"    = c("Aw (South Asia)","Aw (Other)")
  )
  
  out_plots <- list()
  
  for (current_group in names(combined_groups)) {
    groups <- combined_groups[[current_group]]
    message(paste("Processing group:", current_group))
    
    # pick cities that belong to the target plot groups
    cities_in_group <- dplyr::filter(city_data, PlotGroup %in% groups)
    
    # optional: enforce display order
    if (!is.null(desired_order_afam) && current_group == "Af+Am") {
      cities_in_group$City <- factor(cities_in_group$City, levels = desired_order_afam)
      cities_in_group <- dplyr::arrange(cities_in_group, City)
    }
    if (!is.null(desired_order_aw) && current_group == "Aw") {
      cities_in_group$City <- factor(cities_in_group$City, levels = desired_order_aw)
      cities_in_group <- dplyr::arrange(cities_in_group, City)
    }
    
    num_plots <- nrow(cities_in_group)
    if (num_plots == 0) {
      message(paste("  -> No cities for group:", current_group))
      out_plots[[current_group]] <- list()
      next
    }
    
    num_cols <- min(num_plots, num_cols_max)
    num_rows <- ceiling(num_plots / num_cols)
    
    plot_list <- list()
    
    for (j in seq_len(num_plots)) {
      current_city <- as.character(cities_in_group$City[j])
      target_temp  <- cities_in_group$TargetTemp[j]
      climate_grp  <- cities_in_group$ClimateGroup[j]
      message(paste("  - Generating map for:", current_city, "at", target_temp, "\u2103"))
      
      filtered_data <- dplyr::filter(all_metrics_bh, City == current_city, MaxOutdoorTemp == target_temp)
      if (nrow(filtered_data) < 3) {
        message(paste("    -> Skipping", current_city, "(Not enough data points)"))
        next
      }
      max_point <- filtered_data |>
        dplyr::filter(ActualOKHours == max(ActualOKHours, na.rm = TRUE)) |>
        dplyr::slice(1)
      filtered_data_clean <- dplyr::filter(filtered_data, is.finite(MET) & is.finite(CLO) & is.finite(ActualOKHours))
      if (nrow(filtered_data_clean) < 3) {
        message(paste("    -> Skipping", current_city, "(Not enough finite data points)"))
        next
      }
      
      # ---- Interpolation ----
      interp_result <- with(filtered_data_clean, akima::interp(x = MET, y = CLO, z = ActualOKHours, nx = 100, ny = 100))
      interp_df <- as.data.frame(akima::interp2xyz(interp_result))
      colnames(interp_df) <- c("MET", "CLO", "ActualOKHours")
      
      contour_breaks <- seq(0, fill_max, by = contour_by)
      
      p <- ggplot2::ggplot(interp_df, ggplot2::aes(x = MET, y = CLO)) +
        ggplot2::geom_tile(ggplot2::aes(fill = ActualOKHours)) +
        ggplot2::geom_contour(ggplot2::aes(z = ActualOKHours),
                              breaks = contour_breaks, color = "gray40",
                              alpha = 0.6, linewidth = 0.5) +
        metR::geom_text_contour(ggplot2::aes(z = ActualOKHours),
                                breaks = contour_breaks, stroke = 0.2,
                                stroke.color = "white", size = 4, skip = 0) +
        ggplot2::geom_point(data = max_point, color = "black", fill = "white",
                            size = 4.5, shape = 21) +
        ggplot2::geom_text(data = max_point,
                           ggplot2::aes(label = round(ActualOKHours)),
                           fontface = "bold", color = "black", nudge_y = 0.015) +
        ggplot2::scale_fill_gradient(
          low = "white", high = "#A6D854",
          limits = c(0, 2000), name = "Comfort\nHours",
          oob = scales::squish
        ) +
        ggplot2::coord_cartesian(xlim = c(0.8, 1.8), expand = FALSE) +
        ggplot2::labs(x = "MET", y = "CLO") +
        # ---- Label in-panel: "City-Climate-Temp" ----
        ggplot2::annotate(
          "text", x = 0.82, y = Inf,
          label = paste0(current_city, "(", climate_grp, ") - ", target_temp, "\u2103"),
          hjust = 0, vjust = 1.5, size = 6, fontface = "bold"
        ) +
        ggplot2::theme_minimal(base_size = 12) +
        ggplot2::theme(
          plot.title = ggplot2::element_text(face = "bold", size = 14),
          legend.position = "right",
          axis.text.x = ggplot2::element_text(size = 12),
          axis.text.y = ggplot2::element_text(size = 12)
        ) +
        + ggplot2::guides(
          fill = ggplot2::guide_colorbar(
            title.position = "top",
            title.hjust = 0.5,
            barheight = grid::unit(2.5, "mm"),  # thinner legend bar
            barwidth  = grid::unit(45, "mm")    # adjust length 
          )
        )
      
      # ---- Trim axes for interior panels ----
      col_pos <- (j - 1) %% num_cols + 1
      row_pos <- ceiling(j / num_cols)
      if (col_pos != 1) {
        p <- p + ggplot2::theme(
          axis.title.y = ggplot2::element_blank(),
          axis.text.y  = ggplot2::element_blank(),
          axis.ticks.y = ggplot2::element_blank()
        )
      }
      if (row_pos != num_rows) {
        p <- p + ggplot2::theme(
          axis.title.x = ggplot2::element_blank(),
          axis.text.x  = ggplot2::element_blank(),
          axis.ticks.x = ggplot2::element_blank()
        )
      }
      plot_list[[current_city]] <- p
    }
    
    # ---- Save a combined plot per group (Af+Am or Aw) ----
    if (length(plot_list) > 0) {
      combined_plot <- patchwork::wrap_plots(plot_list, ncol = num_cols, guides = 'collect') +
        patchwork::plot_annotation(theme = ggplot2::theme(
          plot.title = ggplot2::element_text(size = 16, face = "bold", hjust = 0.5)
        )) & ggplot2::theme(legend.position = 'right')
      
      sanitized_group_name <- gsub("[^a-zA-Z0-9_+]", "_", current_group)
      file_name <- paste0("ComfortMap_Group_", sanitized_group_name, ".png")
      file_path <- file.path(output_dir_base, file_name)
      
      ggplot2::ggsave(
        filename = file_path,
        plot = combined_plot,
        width = 3.5 * num_cols,
        height = 3.5 * ceiling(length(plot_list)/num_cols),
        dpi = 300, bg = "white", limitsize = FALSE
      )
      message(paste("  -> Combined plot saved to", file_path))
      out_plots[[current_group]] <- plot_list
    } else {
      message(paste("  -> No plots were generated for group:", current_group))
      out_plots[[current_group]] <- list()
    }
  }
  
  invisible(out_plots)
}
# ---- End ----

# run_daytime_maps
desired_order_afam <- c(
  "Guam","Honiara","KualaLumpur","Singapore",        # Af
  "Freetown","Jakarta","Lagos","Manila","Miami","SantoDomingo" # Am
)

desired_order_aw <- c( 
  "Bangkok","Mumbai","Chennai","RioDeJaneiro","Darwin",
  "Kolkata","Bengaluru","Hyderabad","Honolulu","Dhaka"
)

plot_clomet_maps_daytime(
  all_metrics_bh = all_metrics_bh,
  city_climate_mapping = city_climate_mapping,
  optimal_temps = optimal_temps,
  desired_order_afam = desired_order_afam,
  desired_order_aw   = desired_order_aw
)
# ---- End ----
