---
title: "R Notebook"
# Author: Kazuki Horikoshi
# Date: 12/9/2024
# Description: Analyzing NV hours based on increased velocity
---
```{r}
# Load libraries
```


# --------------- Clear your environment --------------
rm(list = ls())

# ------------------ Preparation -----------------------
# Preparation: import the libraries
# Preparation: install libraries if not available

# options(timeout = 2000)

library(tidyverse)
library(ggplot2)
library(lubridate)
library(dplyr)
library(here)
library(data.table)
library(doParallel)
library(foreach)
library(scales)
library(reticulate)
library(DBI)
library(RSQLite)
library(tidyr)
library(patchwork)
library(doSNOW)
library(progress)
library(RColorBrewer)
library(akima)
library(metR)
library(scales)
library(grid)


# ################
use_python("/usr/bin/python3", required = TRUE)
py_config()
# Load Python library
pythermalcomfort <- import("pythermalcomfort")

path <- here()

library(eplusr)
ver <- "9.5.0"
idd <- use_idd(ver, download = "auto")

# -- Define conversion factors and constants --
# 1 sq ft = 0.092903 sq m
AREA_FT2 <- 21609.96
AREA_M2 <- AREA_FT2 * 0.092903
KBTU_TO_KWH <- 0.293071

# Display all available color palettes from RColorBrewer for reference
display.brewer.all()
# The "Set2" palette has 8 colors. We load them all.
set2_colors <- brewer.pal(n = 8, name = "Set2")
# ---- End ----


# ---- Set Region Mapping ----

city_climate_mapping <- data.frame(
  City = c(
    "Singapore", "KualaLumpur", "SantoDomingo", "Honolulu", "Freetown", "Guam", "Honiara",
    "Manila", "Dhaka", "Miami", "Jakarta", "Lagos",
    "Bangkok", "Mumbai", "Chennai", "RioDeJaneiro", "Darwin", "Kolkata", "Bengaluru", "Hyderabad"
  ),
  ClimateGroup = c(
    "Af", "Af", "Am", "Aw", "Am", "Af", "Af",
    "Am", "Aw", "Am", "Am", "Am",
    "Aw", "Aw", "Aw", "Aw", "Aw", "Aw", "Aw", "Aw"
  )
)
# ---- End ----

# split Aw group into south asia and others
south_asian_cities <- c("Mumbai", "Chennai", "Kolkata", "Bengaluru", "Hyderabad", "Dhaka")
city_climate_mapping <- city_climate_mapping %>%
  mutate(PlotGroup = case_when(
    City %in% south_asian_cities ~ "Aw (South Asia)",
    ClimateGroup == "Aw" ~ "Aw (Other)",
    TRUE ~ ClimateGroup
  ))

plot_groups <- c("Af", "Am", "Aw (South Asia)", "Aw (Other)")

combined_groups <- list(
  "Af+Am" = c("Af", "Am"),
  "Aw" = c("Aw (South Asia)", "Aw (Other)")
)

desired_order_afam <- c(
  "Guam", "Honiara", "KualaLumpur", "Singapore", # Af
  "Freetown", "Jakarta", "Lagos", "Manila", "Miami", "SantoDomingo" # Am
)

# Optional order for Aw
desired_order_aw <- c(
  "Bangkok", "Mumbai", "Chennai", "RioDeJaneiro", "Darwin",
  "Kolkata", "Bengaluru", "Hyderabad", "Honolulu", "Dhaka"
)

# optimal temperature for NV in each city (daytime NV case)
optimal_temps <- c(
  Guam = 29, Honiara = 30, KualaLumpur = 29, Singapore = 29, Freetown = 30,
  Jakarta = 30, Lagos = 30, Manila = 29, Miami = 29, SantoDomingo = 30,
  Bengaluru = 32, Chennai = 30, Dhaka = 29, Hyderabad = 32, Kolkata = 29,
  Mumbai = 29, Bangkok = 29, Darwin = 30, Honolulu = 30, RioDeJaneiro = 31
)
optimal_temps_df <- stack(optimal_temps)
colnames(optimal_temps_df) <- c("TargetTemp", "City")

city_temp_list <- tibble::deframe(optimal_temps_df[, c("City", "TargetTemp")])

# Merge climate data and optimal temps
city_data <- merge(city_climate_mapping, optimal_temps_df, by = "City")
city_data <- city_data %>%
  mutate(PlotGroup = case_when(
    City %in% south_asian_cities ~ "Aw (South Asia)",
    ClimateGroup == "Aw" ~ "Aw (Other)",
    TRUE ~ ClimateGroup
  ))
# ---- End ----

# epw list
epw_dict <- list(
  Bangkok = file.path(
    "~/localdir/analysis/data/epw/Bangkok/THA_CRG_Bangkok.Metropolis.484550_TMYx.2009-2023",
    "THA_CRG_Bangkok.Metropolis.484550_TMYx.2009-2023.epw"
  ),
  Bengaluru = file.path(
    "~/localdir/analysis/data/epw/Bengaluru/IND_KA_Bengaluru-Hindustan.AP.432960_TMYx.2004-2018",
    "IND_KA_Bengaluru-Hindustan.AP.432960_TMYx.2004-2018.epw"
  ),
  Chennai = file.path(
    "~/localdir/analysis/data/epw/Chennai/IND_TN_Chennai.Intl.AP.432790_TMYx.2009-2023",
    "IND_TN_Chennai.Intl.AP.432790_TMYx.2009-2023.epw"
  ),
  Darwin = file.path(
    "~/localdir/analysis/data/epw/Darwin/AUS_NT_Darwin_Intl_AP_941200_TMYx_2009-2023",
    "AUS_NT_Darwin_Intl_AP_941200_TMYx_2009-2023.epw"
  ),
  Dhaka = file.path(
    "~/localdir/analysis/data/epw/Dhaka/BGD_DH_Dhaka-Shahjalal.Intl.AP.419220_TMYx.2009-2023",
    "BGD_DH_Dhaka-Shahjalal.Intl.AP.419220_TMYx.2009-2023.epw"
  ),
  Freetown = file.path(
    "~/localdir/analysis/data/epw/Freetown/SLE_NO_Lungi.Intl.AP.618560_TMYx.2009-2023",
    "SLE_NO_Lungi.Intl.AP.618560_TMYx.2009-2023.epw"
  ),
  Guam = file.path(
    "~/localdir/analysis/data/epw/Guam/GUM_TM_Tamuning-Won.Pat.Intl.AP.912120_TMYx.2009-2023",
    "GUM_TM_Tamuning-Won.Pat.Intl.AP.912120_TMYx.2009-2023.epw"
  ),
  Honiara = file.path(
    "~/localdir/analysis/data/epw/Honiara/SLB_GU_Honiara.Intl.AP.915200_TMYx.2009-2023",
    "SLB_GU_Honiara.Intl.AP.915200_TMYx.2009-2023.epw"
  ),
  Honolulu = file.path(
    "~/localdir/analysis/data/epw/Honolulu/USA_HI_Honolulu-Inouye.Intl.AP.Oahu.911820_TMYx.2009-2023",
    "USA_HI_Honolulu-Inouye.Intl.AP.Oahu.911820_TMYx.2009-2023.epw"
  ),
  Hyderabad = file.path(
    "~/localdir/analysis/data/epw/Hyderabad/IND_TG_Hyderabad-Gandhi.Intl.AP.431285_TMYx.2009-2023",
    "IND_TG_Hyderabad-Gandhi.Intl.AP.431285_TMYx.2009-2023.epw"
  ),
  Jakarta = file.path(
    "~/localdir/analysis/data/epw/Jakarta/IDN_JW_Jakarta-Soekarno-Hatta.Intl.AP.967490_TMYx.2009-2023",
    "IDN_JW_Jakarta-Soekarno-Hatta.Intl.AP.967490_TMYx.2009-2023.epw"
  ),
  Kinshasa = file.path(
    "~/localdir/analysis/data/epw/Kinshasa/COD_KN_Kinshasa-Ndjili.Intl.AP.642100_TMYx.2009-2023",
    "COD_KN_Kinshasa-Ndjili.Intl.AP.642100_TMYx.2009-2023.epw"
  ),
  Kolkata = file.path(
    "~/localdir/analysis/data/epw/Kolkata/IND_WB_Kolkata-Bose.Intl.AP.428090_TMYx.2009-2023",
    "IND_WB_Kolkata-Bose.Intl.AP.428090_TMYx.2009-2023.epw"
  ),
  KualaLumpur = file.path(
    "~/localdir/analysis/data/epw/KualaLumpur/MYS_KL_Kuala.Lumpur-Subang-Abdul.Aziz.Shah.Intl.AP.486470_TMYx.2009-2023",
    "MYS_KL_Kuala.Lumpur-Subang-Abdul.Aziz.Shah.Intl.AP.486470_TMYx.2009-2023.epw"
  ),
  Lagos = file.path(
    "~/localdir/analysis/data/epw/Lagos/NGA_LA_Lagos-Muhammed.Intl.AP.652010_TMYx.2009-2023",
    "NGA_LA_Lagos-Muhammed.Intl.AP.652010_TMYx.2009-2023.epw"
  ),
  Manila = file.path(
    "~/localdir/analysis/data/epw/Manila/PHL_NCR_Manila.984250_TMYx.2009-2023",
    "PHL_NCR_Manila.984250_TMYx.2009-2023.epw"
  ),
  Miami = file.path(
    "~/localdir/analysis/data/epw/Miami/USA_FL_Miami.Intl.AP.722020_US.Normals.2006-2020",
    "USA_FL_Miami.Intl.AP.722020_US.Normals.2006-2020.epw"
  ),
  Mumbai = file.path(
    "~/localdir/analysis/data/epw/Mumbai/IND_MH_Mumbai-Shivaji.Intl.AP.430030_TMYx.2009-2023",
    "IND_MH_Mumbai-Shivaji.Intl.AP.430030_TMYx.2009-2023.epw"
  ),
  RioDeJaneiro = file.path(
    "~/localdir/analysis/data/epw/RioDeJaneiro/BRA_RJ_Rio.de.Janeiro-Galeao-Jobim.Intl.AP.837460_TMYx.2009-2023",
    "BRA_RJ_Rio.de.Janeiro-Galeao-Jobim.Intl.AP.837460_TMYx.2009-2023.epw"
  ),
  SantoDomingo = file.path(
    "~/localdir/analysis/data/epw/SantoDomingo/DOM_NC_Santo.Domingo.784860_TMYx.2009-2023",
    "DOM_NC_Santo.Domingo.784860_TMYx.2009-2023.epw"
  ),
  Singapore = file.path(
    "~/localdir/analysis/data/epw/Singapore/SGP_SINGAPORE-CHANGI-IAP_486980S_23",
    "SGP_SINGAPORE-CHANGI-IAP_486980S_23.epw"
  )
)
# ---- End ----

# Loading settings file
source("config.R")

```{r}
# Calculate Lower Threshold(No need to run everytime)
```

<!-- # ------------------------------------------------------------------------------ -->
<!-- # 1. Define Calculation Formula for Adaptive Comfort -->
<!-- # Formula: Tlow = 0.31 * Tout_mean + 17.8 - 3.5 -->
<!-- # (0.5 * 7 = 3.5 for the lower boundary of the 80% acceptability limit) -->
<!-- # ------------------------------------------------------------------------------ -->
<!-- calculate_tlow <- function(tout_mean) { -->
<!--   return(0.31 * tout_mean + 14.3) -->
<!-- } -->

<!-- # ------------------------------------------------------------------------------ -->
<!-- # 2. Extract and Calculate Monthly Data for All Cities -->
<!-- # ------------------------------------------------------------------------------ -->
<!-- summary_list <- imap(epw_dict, function(path, city_name) { -->

<!--   # EPW hourly data starts at line 9 (skip first 8 header lines) -->
<!--   # Column 2 = Month, Column 7 = Dry Bulb Temperature (Celsius) -->
<!--   # We use data.table::fread for high-speed, direct reading -->
<!--   epw_raw <- data.table::fread(path, skip = 8, header = FALSE) -->

<!--   # Extract relevant columns and rename for clarity -->
<!--   # V2 is Month, V7 is Dry Bulb Temp -->
<!--   monthly_stats <- epw_raw[, .( -->
<!--     Mean_Tout = mean(V7) -->
<!--   ), by = .(month = V2)] -->

<!--   # Compute the corresponding Tlow for each month -->
<!--   monthly_stats[, `:=`( -->
<!--     City = city_name, -->
<!--     Tlow = calculate_tlow(Mean_Tout) -->
<!--   )] -->

<!--   return(monthly_stats) -->
<!-- }) -->

<!-- # ------------------------------------------------------------------------------ -->
<!-- # 3. Combine All Results into a Single Dataframe -->
<!-- # ------------------------------------------------------------------------------ -->
<!-- all_city_tlow_df <- bind_rows(summary_list) %>% -->
<!--   select(City, month, Mean_Tout, Tlow) -->

<!-- # ------------------------------------------------------------------------------ -->
<!-- # 4. Convert to "Wide" Format for Publication/Report -->
<!-- # Reshaping so that each month (1-12) becomes a column -->
<!-- # ------------------------------------------------------------------------------ -->
<!-- tlow_table_wide <- all_city_tlow_df %>% -->
<!--   select(City, month, Tlow) %>% -->
<!--   mutate(Tlow = round(Tlow, 2)) %>% -->
<!--   pivot_wider( -->
<!--     names_from = month,  -->
<!--     names_prefix = "Month_",  -->
<!--     values_from = Tlow -->
<!--   ) -->

<!-- # ------------------------------------------------------------------------------ -->
<!-- # 5. Export to CSV -->
<!-- # ------------------------------------------------------------------------------ -->
<!-- output_csv <- "Monthly_Tlow_Summary_All_Cities.csv" -->
<!-- write.csv(tlow_table_wide, output_csv, row.names = FALSE) -->

<!-- cat(sprintf("\n[Success] Monthly lower limit temperatures summarized and saved to: %s\n", output_csv)) -->


```{r}
# E+ function with low-outdoor temp threshold as variable
```
<!-- # NV Analysis Pipeline -->
<!-- # Part 1: Run EnergyPlus Simulation with Varying MaxOutdoorTemp -->

<!-- # ------------------------------------------------------------------------------ -->
<!-- # Helper Function: Build ERL string for monthly Tlow logic -->
<!-- # ------------------------------------------------------------------------------ -->
<!-- build_monthly_tlow_text <- function(city_name, tlow_df) { -->
<!--   city_row <- tlow_df[tlow_df$City == city_name, ] -->

<!--   lines <- c( -->
<!--     "", -->
<!--     "EnergyManagementSystem:Program,", -->
<!--     "    CalculateMonthlyTlow,    !- Name", -->
<!--     "    SET CurrentMonth = Month,!- Program Line 1" -->
<!--   ) -->

<!--   for (m in 1:12) { -->
<!--     val <- city_row[[paste0("Month_", m)]] -->
<!--     prefix <- if (m == 1) "IF" else "ELSEIF" -->
<!--     lines <- c(lines, sprintf("    %s CurrentMonth == %d, SET Tlow_Current = %.2f,", prefix, m, val)) -->
<!--   } -->

<!--   lines <- c(lines, "    ENDIF;                   !- End", "") -->
<!--   return(paste(lines, collapse = "\n")) -->
<!-- } -->

<!-- # ------------------------------------------------------------------------------ -->
<!-- # Helper Function:TEXT REPLACEMENT FUNCTION -->
<!-- # ------------------------------------------------------------------------------ -->

<!-- # ---- replace_ems_if_line_in_idf ---------------------------------------------- -->
<!-- # Purpose: -->
<!-- #   Replace ONLY "Program Line 1" (IF line) for a given EMS Program by plain text. -->
<!-- # How it works: -->
<!-- #   - Finds block that starts with: EnergyManagementSystem:Program, <ProgramName> -->
<!-- # Notes: -->
<!-- #   - Keeps the comma at the end, preserves other lines as-is. -->
<!-- #   - Backup is created automatically: <file_out>.bak -->
<!-- replace_ems_with_dynamic_logic <- function(file_path, program_name, cond_expr) { -->
<!--   txt <- readLines(file_path, warn = FALSE) -->

<!--   start_pat <- "^\\s*EnergyManagementSystem:Program\\s*,\\s*$" -->
<!--   name_pat  <- paste0("^\\s*", gsub("([\\^\\$\\*\\+\\?\\(\\)\\[\\]\\{\\}\\.\\|\\\\])", "\\\\\\1", program_name), "\\s*,") -->

<!--   n <- length(txt); i <- 1L; found <- FALSE -->
<!--   while (i <= n) { -->
<!--     if (grepl(start_pat, txt[i], ignore.case = TRUE)) { -->
<!--       j <- i + 1L -->
<!--       while (j <= n && grepl("^\\s*$", txt[j])) j <- j + 1L  -->
<!--       if (j <= n && grepl(name_pat, txt[j], ignore.case = TRUE)) { -->
<!--         # 以前成功した手法に基づき、Program Line 1と2を書き換える -->
<!--         # RUN命令と新しいIF条件を確実に挿入 -->
<!--         txt[j + 1] <- "    RUN CalculateMonthlyTlow," -->
<!--         txt[j + 2] <- paste0("    IF ", cond_expr, ",") -->
<!--         found <- TRUE; break -->
<!--       } -->
<!--     } -->
<!--     i <- i + 1L -->
<!--   } -->
<!--   writeLines(txt, file_path) -->
<!-- } -->


<!-- # ---- End replace_ems_if_line_in_idf ---- -->

<!-- remove_ems_program_from_text <- function(txt, program_name) { -->
<!--   start_pat <- "^\\s*EnergyManagementSystem:Program\\s*,\\s*$" -->
<!--   name_pat  <- paste0("^\\s*", gsub("([\\^\\$\\*\\+\\?\\(\\)\\[\\]\\{\\}\\.\\|\\\\])", "\\\\\\1", program_name), "\\s*,") -->

<!--   n <- length(txt); i <- 1L -->
<!--   new_txt <- list() -->

<!--   while (i <= n) { -->
<!--     # Programの開始行を見つけた場合 -->
<!--     if (grepl(start_pat, txt[i], ignore.case = TRUE)) { -->
<!--       j <- i + 1L -->
<!--       while (j <= n && grepl("^\\s*$", txt[j])) j <- j + 1L # 空行スキップ -->

<!--       # 名前が一致するか確認 -->
<!--       if (j <= n && grepl(name_pat, txt[j], ignore.case = TRUE)) { -->
<!--         # セミコロンが見つかるまで行をスキップ（削除対象） -->
<!--         k <- j -->
<!--         while (k <= n && !grepl(";", txt[k])) k <- k + 1L -->
<!--         i <- k + 1L # ポインタを削除範囲の次に進める -->
<!--         next -->
<!--       } -->
<!--     } -->
<!--     new_txt <- c(new_txt, txt[i]) -->
<!--     i <- i + 1L -->
<!--   } -->
<!--   return(as.character(new_txt)) -->
<!-- } -->

<!-- # ============================================================================== -->
<!-- # 3. MAIN SIMULATION FUNCTION -->
<!-- # ============================================================================== -->
<!-- run_energyplus_nv_with_tlow <- function(country_name, epw_path, idf_template_path, tlow_df,  -->
<!--                                         natvent_list, hybridvent_list,  -->
<!--                                         save_dir_root = here::here("R.Data"),  -->
<!--                                         max_outdoor_range = 27:32, overwrite = FALSE) { -->

<!--   ver <- "9.5.0"; idd <- eplusr::use_idd(ver, download = "auto") -->

<!--   for (max_outdoor in max_outdoor_range) { -->
<!--     case_label <- paste0("MaxOutdoor_", max_outdoor) -->
<!--     path_cal <- file.path("data", "idf", "12.cals", country_name, case_label) -->
<!--     if (!dir.exists(path_cal)) dir.create(path_cal, recursive = TRUE) -->

<!--     model_path <- file.path(path_cal, "model_updated.idf") -->
<!--     if (file.exists(model_path) && !overwrite) next -->

<!--     # --- Step A: テキスト読み込みとクリーニング --- -->
<!--     idf_text <- readLines(idf_template_path, warn = FALSE) -->

<!--     # 既存の CalculateMonthlyTlow があれば一旦消す（重複防止） -->
<!--     idf_text <- remove_ems_program_from_text(idf_text, "CalculateMonthlyTlow") -->

<!--     # CalculateMonthlyTlowを生成して追加 -->
<!--     new_prog <- build_monthly_tlow_text(country_name, tlow_df) -->
<!--     idf_text <- c(idf_text, new_prog) -->

<!--     # GlobalVariableのチェックと追加（既に無ければ足す） -->
<!--     if (!any(grepl("TLOW_CURRENT", idf_text, ignore.case = TRUE))) { -->
<!--       idf_text <- c(idf_text, "\nEnergyManagementSystem:GlobalVariable,\n    TLOW_CURRENT; !- Variable Name\n") -->
<!--     } -->

<!--     writeLines(idf_text, model_path) -->

<!--     # --- Step B: eplusr で閾値を個別に更新（安定版） --- -->
<!--     idf <- eplusr::read_idf(model_path, idd = idd) -->

<!--     for (name in natvent_list) { -->
<!--       if (idf$is_valid_name(name)) { -->
<!--         idf$object(name)$set(Minimum_Outdoor_Temperature = 10, Maximum_Outdoor_Temperature = max_outdoor) -->
<!--       } -->
<!--     } -->
<!--     for (name in hybridvent_list) { -->
<!--       if (idf$is_valid_name(name)) { -->
<!--         idf$object(name)$set(Minimum_Outdoor_Temperature = 10, Maximum_Outdoor_Temperature = max_outdoor) -->
<!--       } -->
<!--     } -->

<!--     idf$save(model_path, overwrite = TRUE) -->

<!--     # --- Step C: メインIF文の置換（以前成功した方式） --- -->
<!--     nv_cond <- sprintf("(NV_Enable_SchedVal == 1) && (OUTDOORTEMP < %.1f) && (OUTDOORTEMP > Tlow_Current) && (WindSpeed_Sensor <= 10) && (Rain_Sensor == 0)", max_outdoor) -->

<!--     # ここも replace_ems_with_dynamic_logic を使用 -->
<!--     replace_ems_with_dynamic_logic(model_path, "AdjustCoolSetpoint", nv_cond) -->
<!--     replace_ems_with_dynamic_logic(model_path, "AdjustAllListedWindows_Program", nv_cond) -->

<!--     # --- Step D: 実行 --- -->
<!--     cat("[Run] Simulation starting for:", country_name, case_label, "\n") -->
<!--     final_model <- eplusr::read_idf(model_path, idd = idd) -->
<!--     final_model$run(weather = epw_path, dir = path_cal, wait = TRUE) -->
<!--   } -->
<!-- } -->


<!-- ## Setting epw data link and Run E+ -->

<!-- # ---- epw data link configuration ---- -->

<!-- <!-- path_idf <- file.path("data", "idf", "11.setting_edit", "250812_DaytimeOnlyNV", "model_preprocessed.idf") --> -->

<!-- path_idf_template <- file.path("data", "idf", "11.setting_edit", "260107_FlexibleLowerThreshold", "model_preprocessed.idf") -->

<!-- # ---- End ---- -->

<!-- # SG case -->
<!-- path_singapore <- epw_dict[["Singapore"]] -->

<!-- cat("\n=== Running simulation for: Singapore ===\n") -->
<!-- run_energyplus_nv_with_tlow( -->
<!--     country_name = "Singapore", -->
<!--     epw_path = path_singapore, -->
<!--     idf_template_path = path_idf_template, -->
<!--     tlow_df = tlow_master_df,  # Use the pre-loaded Tlow CSV data -->
<!--     max_outdoor_range = 27:32, -->
<!--     overwrite = FALSE, -->
<!--     natvent_list=natvent_list, -->
<!--     hybridvent_list=hybridvent_list -->
<!--   ) -->

<!-- # ---- End ---- -->

```{r}
# Run E+ With fixed lower threshold
```

replace_ems_if_line_in_idf <- function(file_in, file_out, program_name, cond_expr) {
  # read
  txt <- readLines(file_in, warn = FALSE)
  # backup
  if (file.exists(file_out)) {
    file.copy(file_out, paste0(file_out, ".bak"), overwrite = TRUE)
  }

  # patterns (strict but simple)
  start_pat <- paste0("^\\s*EnergyManagementSystem:Program\\s*,\\s*$")
  name_pat <- paste0(
    "^\\s*",
    gsub("([\\^\\$\\*\\+\\?\\(\\)\\[\\]\\{\\}\\.\\|\\\\])", "\\\\\\1", program_name),
    "\\s*,\\s*(?:!-.*)?$"
  )

  n <- length(txt)
  i <- 1L
  found <- FALSE
  replaced <- FALSE

  while (i <= n) {
    # find "EnergyManagementSystem:Program," line
    if (grepl(start_pat, txt[i])) {
      # next non-empty must be the Name line
      j <- i + 1L
      while (j <= n && grepl("^\\s*$", txt[j])) j <- j + 1L
      if (j <= n && grepl(name_pat, txt[j])) {
        found <- TRUE
        # find next non-empty (Program Line 1)
        k <- j + 1L
        while (k <= n && grepl("^\\s*$", txt[k])) k <- k + 1L
        if (k <= n) {
          # build new IF line with trailing comma
          new_line <- paste0("    IF ", cond_expr, ",")
          txt[k] <- new_line
          replaced <- TRUE
        }
        # Exit after finding one program (assuming no duplicate names)
        break
      }
    }
    i <- i + 1L
  }

  if (!found) stop(sprintf("Program '%s' was not found in IDF text.", program_name))
  if (!replaced) stop(sprintf("Program '%s' IF line could not be replaced.", program_name))

  writeLines(txt, file_out, useBytes = TRUE)
  invisible(TRUE)
}

# replace_ems_if_and_set_in_idf
# ----
replace_ems_if_and_set_in_idf <- function(file_in, file_out, program_name, cond_expr,
                                         set_var = NULL, set_value = NULL) {
  txt <- readLines(file_in, warn = FALSE)
  if (file.exists(file_out)) file.copy(file_out, paste0(file_out, ".bak"), overwrite = TRUE)

  start_pat <- "^\\s*EnergyManagementSystem:Program\\s*,\\s*(?:!-.*)?$"
  name_pat <- paste0("^\\s*",
                     gsub("([\\^\\$\\*\\+\\?\\(\\)\\[\\]\\{\\}\\.\\|\\\\])", "\\\\\\1", program_name),
                     "\\s*,\\s*(?:!-.*)?$")
  if_pat <- "^\\s*IF\\b"
  set_pat <- if (!is.null(set_var)) paste0("^\\s*SET\\s+", gsub("([\\^\\$\\*\\+\\?\\(\\)\\[\\]\\{\\}\\.\\|\\\\])", "\\\\\\1", set_var), "\\s*=") else NULL

  n <- length(txt)
  i <- 1L
  found <- FALSE
  replaced_if <- FALSE
  replaced_set <- FALSE

  while (i <= n) {
    if (grepl(start_pat, txt[i])) {
      j <- i + 1L
      while (j <= n && grepl("^\\s*$", txt[j])) j <- j + 1L

      if (j <= n && grepl(name_pat, txt[j])) {
        found <- TRUE

        # define block end (line containing ';')
        end <- j + 1L
        while (end <= n && !grepl(";", txt[end])) end <- end + 1L
        if (end > n) stop(sprintf("Program '%s' block end ';' not found.", program_name))

        # scan within block
        k <- j + 1L
        while (k <= end) {
          if (!replaced_if && grepl(if_pat, txt[k])) {
            txt[k] <- paste0("    IF ", cond_expr, ",")
            replaced_if <- TRUE
          } else if (!is.null(set_pat) && !replaced_set && grepl(set_pat, txt[k])) {
            # keep trailing comment if any
            comment <- sub("^.*?(\\s*!-.*)$", "\\1", txt[k])
            has_comment <- grepl("!-", txt[k])
            new_set <- paste0("    SET ", set_var, " = ", sprintf("%.1f", set_value), ",")
            txt[k] <- if (has_comment) paste0(new_set, "  ", comment) else new_set
            replaced_set <- TRUE
          }
          k <- k + 1L
        }
        break
      }
    }
    i <- i + 1L
  }

  if (!found) stop(sprintf("Program '%s' was not found in IDF text.", program_name))
  if (!replaced_if) stop(sprintf("Program '%s' IF line could not be replaced.", program_name))
  if (!is.null(set_pat) && !replaced_set) stop(sprintf("Program '%s' SET line for '%s' not found.", program_name, set_var))

  writeLines(txt, file_out, useBytes = TRUE)
  invisible(TRUE)
}
# ---- End ----

# ---- NV function definition ----
## Purpose:
##   Update NV/HV thresholds and rewrite EMS to use:
##   (NV_Enable_SchedVal == 1) AND (OutdoorTemp < MaxOutdoorTemp)
##   AND (WindSpeed_Sensor <= MaxWindSpeed) AND (Rain_Sensor == 0)
##   for both setpoint switching and window actuation.
## Notes:
##   - Keeps your existing Open/Close lines in the windows program; only fixes IF line.
##   - No hysteresis in this version.
run_energyplus_nv <- function(country_name,
                              epw_path,
                              idf_template_path,
                              save_dir_root = here::here("R.Data"),
                              max_outdoor_range = 27:32,
                              overwrite = FALSE) {

  ver <- "9.5.0"
  idd <- eplusr::use_idd(ver, download = "auto")

# Object names (unchanged)
natvent_list <- c(
  "NatVent_unit1_FrontRow_BottomFloor", "NatVent_unit2_FrontRow_BottomFloor", "NatVent_unit3_FrontRow_BottomFloor",
  "NatVent_unit1_BackRow_BottomFloor", "NatVent_unit2_BackRow_BottomFloor", "NatVent_unit3_BackRow_BottomFloor",
  "NatVent_unit1_FrontRow_MiddleFloor", "NatVent_unit2_FrontRow_MiddleFloor", "NatVent_unit3_FrontRow_MiddleFloor",
  "NatVent_unit1_BackRow_MiddleFloor", "NatVent_unit2_BackRow_MiddleFloor", "NatVent_unit3_BackRow_MiddleFloor",
  "NatVent_unit1_FrontRow_TopFloor", "NatVent_unit2_FrontRow_TopFloor", "NatVent_unit3_FrontRow_TopFloor",
  "NatVent_unit1_BackRow_TopFloor", "NatVent_unit2_BackRow_TopFloor", "NatVent_unit3_BackRow_TopFloor"
)

hybridvent_list <- c(
  "HybridVentilation_Control_unit1_FrontRow_BottomFloor", "HybridVentilation_Control_unit2_FrontRow_BottomFloor", "HybridVentilation_Control_unit3_FrontRow_BottomFloor",
  "HybridVentilation_Control_unit1_BackRow_BottomFloor", "HybridVentilation_Control_unit2_BackRow_BottomFloor", "HybridVentilation_Control_unit3_BackRow_BottomFloor",
  "HybridVentilation_Control_unit1_FrontRow_MiddleFloor", "HybridVentilation_Control_unit2_FrontRow_MiddleFloor", "HybridVentilation_Control_unit3_FrontRow_MiddleFloor",
  "HybridVentilation_Control_unit1_BackRow_MiddleFloor", "HybridVentilation_Control_unit2_BackRow_MiddleFloor", "HybridVentilation_Control_unit3_BackRow_MiddleFloor",
  "HybridVentilation_Control_unit1_FrontRow_TopFloor", "HybridVentilation_Control_unit2_FrontRow_TopFloor", "HybridVentilation_Control_unit3_FrontRow_TopFloor",
  "HybridVentilation_Control_unit1_BackRow_TopFloor", "HybridVentilation_Control_unit2_BackRow_TopFloor", "HybridVentilation_Control_unit3_BackRow_TopFloor"
)

  for (max_outdoor in max_outdoor_range) {
    case_label <- paste0("MaxOutdoor_", max_outdoor)
    path_cal <- file.path("data", "idf", "12.cals", country_name, case_label)
    if (!dir.exists(path_cal)) dir.create(path_cal, recursive = TRUE)

    model_path <- file.path(path_cal, "model_updated.idf")
    if (file.exists(model_path) && !overwrite) {
      cat("[Skip] Simulation already exists for:", case_label, "\n")
      next
    }

    # --- Step 1: copy template to working file (overwrite this case) ------------
    file.copy(idf_template_path, model_path, overwrite = TRUE)

    # --- Step 2: replace ONLY EMS IF line by text (no eplusr object ops) -------
    max_wind_speed <- 10
    max_indoor_temp <- max_outdoor + 5
    cond_expr <- sprintf(
      "(NV_Enable_SchedVal == 1) && (OUTDOORTEMP < %.1f) && (WindSpeed_Sensor <= %.1f) && (Rain_Sensor == 0)",
      max_outdoor, max_wind_speed
    )
    replace_ems_if_and_set_in_idf(
      model_path, model_path,
      program_name = "AdjustCoolSetpoint",
      cond_expr = cond_expr,
      set_var = "ThermostatCoolSet_Actuator",
      set_value = max_indoor_temp
    )
    
    replace_ems_if_and_set_in_idf(
      model_path, model_path,
      program_name = "AdjustAllListedWindows_Program",
      cond_expr = cond_expr
    )

    # --- Step 3: open via eplusr, update thresholds as before -------------------
    idf <- eplusr::read_idf(model_path, idd = idd)

    min_outdoor_temp <- 20
    max_outdoor_temp <- max_outdoor
    min_indoor_temp <- 20
    max_indoor_temp <- max_outdoor + 5
    # max_wind_speed already set (10)
    min_outdoor_ent <- 1000
    max_outdoor_ent <- 100000
    min_outdoor_dew <- 10
    max_outdoor_dew <- 30

    # ZoneVentilation thresholds (your original indexing method)
    for (name in natvent_list) {
      tmp <- idf$`ZoneVentilation:DesignFlowRate`[[name]]
      dt <- data.table::rbindlist(c(
        list(tmp$to_table()),
        lapply(tmp$ref_to_object(), function(x) x$to_table())
      ))
      dt[16, 6] <- min_indoor_temp
      dt[18, 6] <- max_indoor_temp
      dt[22, 6] <- min_outdoor_temp
      dt[24, 6] <- max_outdoor_temp
      dt[26, 6] <- max_wind_speed
      idf$update(dt)
    }

    # HybridVentilation thresholds (your original indexing method)
    for (name in hybridvent_list) {
      tmp <- idf$`AvailabilityManager:HybridVentilation`[[name]]
      dt <- data.table::rbindlist(c(
        list(tmp$to_table()),
        lapply(tmp$ref_to_object(), function(x) x$to_table())
      ))
      dt[7, 6] <- min_outdoor_temp
      dt[8, 6] <- max_outdoor_temp
      dt[9, 6] <- min_outdoor_ent
      dt[10, 6] <- max_outdoor_ent
      dt[6, 6] <- max_wind_speed
      dt[11, 6] <- min_outdoor_dew
      dt[12, 6] <- max_outdoor_dew
      idf$update(dt)
    }

    # --- Step 4: save & run -----------------------------------------------------
    eplusr::with_silent(idf$save(model_path, overwrite = TRUE))
    cat("[Run] Starting simulation for:", case_label, "\n")
    model <- eplusr::read_idf(model_path, idd = idd)
    invisible(model$run(weather = epw_path, dir = path_cal, wait = TRUE))
  }
}
# ---- End run_energyplus_nv ----

# ---- epw data link configuration ----

path_idf <- file.path("data", "idf", "11.setting_edit", "250812_DaytimeOnlyNV", "model_preprocessed.idf")

# ---- End ----

# SG case
path_singapore <- epw_dict[["Singapore"]]

run_energyplus_nv(
  country_name = "Singapore",
  epw_path = path_singapore,
  idf_template_path = path_idf,
  save_dir_root = here::here("R.Data"),
  max_outdoor_range = 28:32,
  overwrite = FALSE
)

# City-loop case
for (city in names(epw_dict)) {
  epw_path <- epw_dict[[city]]
  cat("\n=== Running simulation for:", city, "===\n")
  run_energyplus_nv(
    country_name = city,
    epw_path = epw_path,
    idf_template_path = path_idf,
    save_dir_root = here("R.Data"),
    max_outdoor_range = 27:32,
    overwrite = FALSE
  )
}

# ---- End ----

```{r}
# e+ parallel calculation
```
natvent_list <- c(
  "NatVent_unit1_FrontRow_BottomFloor", "NatVent_unit2_FrontRow_BottomFloor", "NatVent_unit3_FrontRow_BottomFloor",
  "NatVent_unit1_BackRow_BottomFloor", "NatVent_unit2_BackRow_BottomFloor", "NatVent_unit3_BackRow_BottomFloor",
  "NatVent_unit1_FrontRow_MiddleFloor", "NatVent_unit2_FrontRow_MiddleFloor", "NatVent_unit3_FrontRow_MiddleFloor",
  "NatVent_unit1_BackRow_MiddleFloor", "NatVent_unit2_BackRow_MiddleFloor", "NatVent_unit3_BackRow_MiddleFloor",
  "NatVent_unit1_FrontRow_TopFloor", "NatVent_unit2_FrontRow_TopFloor", "NatVent_unit3_FrontRow_TopFloor",
  "NatVent_unit1_BackRow_TopFloor", "NatVent_unit2_BackRow_TopFloor", "NatVent_unit3_BackRow_TopFloor"
)

hybridvent_list <- c(
  "HybridVentilation_Control_unit1_FrontRow_BottomFloor", "HybridVentilation_Control_unit2_FrontRow_BottomFloor", "HybridVentilation_Control_unit3_FrontRow_BottomFloor",
  "HybridVentilation_Control_unit1_BackRow_BottomFloor", "HybridVentilation_Control_unit2_BackRow_BottomFloor", "HybridVentilation_Control_unit3_BackRow_BottomFloor",
  "HybridVentilation_Control_unit1_FrontRow_MiddleFloor", "HybridVentilation_Control_unit2_FrontRow_MiddleFloor", "HybridVentilation_Control_unit3_FrontRow_MiddleFloor",
  "HybridVentilation_Control_unit1_BackRow_MiddleFloor", "HybridVentilation_Control_unit2_BackRow_MiddleFloor", "HybridVentilation_Control_unit3_BackRow_MiddleFloor",
  "HybridVentilation_Control_unit1_FrontRow_TopFloor", "HybridVentilation_Control_unit2_FrontRow_TopFloor", "HybridVentilation_Control_unit3_FrontRow_TopFloor",
  "HybridVentilation_Control_unit1_BackRow_TopFloor", "HybridVentilation_Control_unit2_BackRow_TopFloor", "HybridVentilation_Control_unit3_BackRow_TopFloor"
)

# run_energyplus_nv_case
# ----
run_energyplus_nv_case <- function(country_name, epw_path, idf_template_path,
                                  max_outdoor, natvent_list, hybridvent_list,
                                  overwrite = FALSE) {
  ver <- "9.5.0"
  idd <- eplusr::use_idd(ver, download = "auto")

  case_label <- paste0("MaxOutdoor_", max_outdoor)
  path_cal <- file.path("data", "idf", "12.cals", country_name, case_label)
  if (!dir.exists(path_cal)) dir.create(path_cal, recursive = TRUE)

  model_path <- file.path(path_cal, "model_updated.idf")
  if (file.exists(model_path) && !overwrite)
    return(list(country = country_name, max_outdoor = max_outdoor, status = "skip", dir = path_cal))

  file.copy(idf_template_path, model_path, overwrite = TRUE)

  max_wind_speed <- 10
  cond_expr <- sprintf("(NV_Enable_SchedVal == 1) && (OUTDOORTEMP < %.1f) && (WindSpeed_Sensor <= %.1f) && (Rain_Sensor == 0)",
                       max_outdoor, max_wind_speed)

  max_indoor_temp <- max_outdoor + 5
  replace_ems_if_and_set_in_idf(model_path, model_path, "AdjustCoolSetpoint",
                                cond_expr, set_var = "ThermostatCoolSet_Actuator", set_value = max_indoor_temp)
  replace_ems_if_and_set_in_idf(model_path, model_path, "AdjustAllListedWindows_Program", cond_expr)

  idf <- eplusr::read_idf(model_path, idd = idd)

  min_outdoor_temp <- 20; max_outdoor_temp <- max_outdoor
  min_indoor_temp <- 20; max_indoor_temp2 <- max_outdoor + 5
  min_outdoor_ent <- 1000; max_outdoor_ent <- 100000
  min_outdoor_dew <- 10; max_outdoor_dew <- 30

  for (name in natvent_list) {
    tmp <- idf$`ZoneVentilation:DesignFlowRate`[[name]]
    dt <- data.table::rbindlist(c(list(tmp$to_table()), lapply(tmp$ref_to_object(), function(x) x$to_table())))
    dt[16, 6] <- min_indoor_temp; dt[18, 6] <- max_indoor_temp2
    dt[22, 6] <- min_outdoor_temp; dt[24, 6] <- max_outdoor_temp
    dt[26, 6] <- max_wind_speed
    idf$update(dt)
  }

  for (name in hybridvent_list) {
    tmp <- idf$`AvailabilityManager:HybridVentilation`[[name]]
    dt <- data.table::rbindlist(c(list(tmp$to_table()), lapply(tmp$ref_to_object(), function(x) x$to_table())))
    dt[7, 6] <- min_outdoor_temp; dt[8, 6] <- max_outdoor_temp
    dt[9, 6] <- min_outdoor_ent; dt[10, 6] <- max_outdoor_ent
    dt[6, 6] <- max_wind_speed
    dt[11, 6] <- min_outdoor_dew; dt[12, 6] <- max_outdoor_dew
    idf$update(dt)
  }

  eplusr::with_silent(idf$save(model_path, overwrite = TRUE))
  model <- eplusr::read_idf(model_path, idd = idd)
  invisible(model$run(weather = epw_path, dir = path_cal, wait = TRUE))

  list(country = country_name, max_outdoor = max_outdoor, status = "done", dir = path_cal)
}
# ---- End ----

# --- 1) cluster once (outside the city loop) ---
num_cores <- parallel::detectCores() - 1
if (num_cores < 1) num_cores <- 1
cl <- makeCluster(num_cores)
registerDoSNOW(cl)

# export once
clusterExport(cl, varlist = c(
  "epw_dict", "path_idf",
  "natvent_list", "hybridvent_list",
  "replace_ems_if_and_set_in_idf",
  "run_energyplus_nv_case"
), envir = environment())

# --- 2) city loop (sequential), inside: parallel over max_outdoor ---
for (city in names(epw_dict)) {
  cat("\n=== Running simulation for:", city, "===\n")

  # optional progress bar per city
  pb <- txtProgressBar(max = length(27:32), style = 3)
  pcount <- 0
  opts <- list(progress = function(n) {pcount <<- pcount + 1; setTxtProgressBar(pb, pcount)})

  res_city <- foreach(max_outdoor = 27:32,
                    .packages = c("eplusr", "data.table", "here"),
                    .errorhandling = "pass") %dopar% {
  run_energyplus_nv_case(
    country_name = city,
    epw_path = epw_dict[[city]],
    idf_template_path = path_idf,
    max_outdoor = max_outdoor,
    natvent_list = natvent_list,
    hybridvent_list = hybridvent_list,
    overwrite = FALSE
    )
  }

  close(pb)
  print(res_city)
}

# --- 3) stop cluster ---
stopCluster(cl)


```{r}
# PMV calculation function
```

<!-- # Vectorizing PMV calculation -->
<!-- py_run_string(" -->
<!-- import numpy as np -->
<!-- from pythermalcomfort.models import pmv -->

<!-- def vectorized_pmv_all(tdb, tr, rh, vr, met, clo): -->
<!--     tdb = np.array(tdb)[:, np.newaxis] -->
<!--     tr  = np.array(tr)[:, np.newaxis] -->
<!--     rh  = np.array(rh)[:, np.newaxis] -->
<!--     vr  = np.array(vr)[np.newaxis, :] -->

<!--     # Ensure inputs are float for pmv -->
<!--     tdb = tdb.astype(float) -->
<!--     tr = tr.astype(float) -->
<!--     rh = rh.astype(float) -->
<!--     vr = vr.astype(float) -->
<!--     met_f = float(met) -->
<!--     clo_f = float(clo) -->

<!--     vec_func = np.vectorize(lambda t, r, h, v: pmv(tdb=t, tr=r, vr=v, rh=h, met=met, clo=clo, limit_inputs=False)) -->
<!--     return vec_func(tdb, tr, rh, vr) -->
<!-- ") -->

<!-- # ---- End ---- -->

<!-- PYTHON_FUNCTION_STRING <- " -->
<!-- import numpy as np -->
<!-- from pythermalcomfort.models import pmv -->

<!-- def vectorized_pmv_all(tdb, tr, rh, vr, met, clo): -->
<!--     tdb = np.asarray(tdb)[:, np.newaxis] -->
<!--     tr  = np.asarray(tr)[:, np.newaxis] -->
<!--     rh  = np.asarray(rh)[:, np.newaxis] -->
<!--     vr  = np.asarray(vr)[np.newaxis, :] -->

<!--     met_f = float(met) -->
<!--     clo_f = float(clo) -->

<!--     vec_func = np.vectorize( -->
<!--         lambda t, r, h, v: pmv(tdb=t, tr=r, vr=v, rh=h, met=met_f, clo=clo_f, limit_inputs=False) -->
<!--     ) -->
<!--     return vec_func(tdb, tr, rh, vr) -->
<!-- " -->

<!-- # Define function in current R session's Python -->
<!-- py_run_string(PYTHON_FUNCTION_STRING) -->


PYTHON_FUNCTION_STRING <- "
import numpy as np
from pythermalcomfort.models import pmv

def vectorized_pmv_all(tdb, tr, rh, vr, met, clo):
    # Rからの入力をNumPy配列に変換
    tdb_arr = np.asarray(tdb)
    tr_arr  = np.asarray(tr)
    rh_arr  = np.asarray(rh)
    vr_arr  = np.asarray(vr) # vrはc(0.1, 0.4...)などのベクトル

    # 結果を格納する行列を準備 (時間数 x 風速数)
    # pythermalcomfort.models.pmv は配列入力を受け取れるので、
    # 各風速ごとに一気に計算させる
    results = []
    for v in vr_arr:
        # この pmv() 呼び出し自体が C 言語レベルで高速にベクトル化されています
        res = pmv(tdb=tdb_arr, tr=tr_arr, vr=v, rh=rh_arr, 
                  met=float(met), clo=float(clo), limit_inputs=False)
        results.append(res)
    
    # 行列として返す (時間 x 風速)
    return np.column_stack(results)
"

```{r}
# PMV for multiple clo, MET setting
```

<!-- ## Before 26 Feb 14, looping for 66 clo/met cases, that is still heavy -->
<!-- # function to analyze NV hours parallel -->
<!-- analyze_nv_from_csv_multiroom_parallel <- function(country_name, -->
<!--                                                     max_outdoor_range = 27:32, -->
<!--                                                     vr_values = c(0.1, 0.4, 0.8, 1.2, 1.6, 2.0), -->
<!--                                                     met_range = seq(0.8, 1.8, by = 0.1), -->
<!--                                                     clo_range = seq(0.3, 0.5, by = 0.04)) { -->

<!--   base_path <- path.expand("~/localdir/analysis/data/idf/12.cals") -->

<!--   room_names <- c( -->
<!--     "LIVING_UNIT1_FRONTROW_BOTTOMFLOOR", "LIVING_UNIT2_FRONTROW_BOTTOMFLOOR", "LIVING_UNIT3_FRONTROW_BOTTOMFLOOR", -->
<!--     "LIVING_UNIT1_BACKROW_BOTTOMFLOOR", "LIVING_UNIT2_BACKROW_BOTTOMFLOOR", "LIVING_UNIT3_BACKROW_BOTTOMFLOOR", -->
<!--     "LIVING_UNIT1_FRONTROW_MIDDLEFLOOR", "LIVING_UNIT2_FRONTROW_MIDDLEFLOOR", "LIVING_UNIT3_FRONTROW_MIDDLEFLOOR", -->
<!--     "LIVING_UNIT1_BACKROW_MIDDLEFLOOR", "LIVING_UNIT2_BACKROW_MIDDLEFLOOR", "LIVING_UNIT3_BACKROW_MIDDLEFLOOR", -->
<!--     "LIVING_UNIT3_BACKROW_TOPFLOOR", "LIVING_UNIT3_FRONTROW_TOPFLOOR", "LIVING_UNIT1_FRONTROW_TOPFLOOR", -->
<!--     "LIVING_UNIT2_BACKROW_TOPFLOOR", "LIVING_UNIT2_FRONTROW_TOPFLOOR", "LIVING_UNIT1_BACKROW_TOPFLOOR" -->
<!--   ) -->

<!--   all_case_results <- list() -->

<!--   for (max_outdoor in max_outdoor_range) { -->
<!--     case_label <- paste0("MaxOutdoor_", max_outdoor) -->
<!--     cat("[Processing] Starting analysis for:", case_label, "\n") -->
<!--     case_start_time <- Sys.time() -->

<!--     path_cal <- file.path(base_path, country_name, case_label) -->
<!--     csv_path <- file.path(path_cal, "model_updated.csv") -->

<!--     if (!file.exists(csv_path)) { -->
<!--       cat("[Skip] CSV file not found:", csv_path, "\n") -->
<!--       next -->
<!--     } -->

<!--     df_csv_original <- read.csv(csv_path, check.names = FALSE, stringsAsFactors = FALSE) -->
<!--     if (nrow(df_csv_original) == 0) { -->
<!--       cat("[Skip] CSV file is empty:", csv_path, "\n") -->
<!--       next -->
<!--     } -->
<!--     colnames(df_csv_original)[1] <- "datetime" -->
<!--     df_csv_original <- df_csv_original[-c(1:288), ] -->

<!--     df_csv_original$datetime <- as.POSIXct( -->
<!--       gsub("  ", " ", df_csv_original$datetime), -->
<!--       format = "%m/%d %H:%M:%S" -->
<!--     ) -->

<!--     df_csv_filtered <- df_csv_original %>% -->
<!--       filter(format(datetime, "%M") == "00") -->

<!--     cat("  [Info] Original timesteps:", nrow(df_csv_original), "-> Filtered to hourly:", nrow(df_csv_filtered), "\n") -->

<!--     col_setpoint <- "LIVING_UNIT1_FRONTROW_BOTTOMFLOOR:Zone Thermostat Cooling Setpoint Temperature [C](TimeStep)" -->
<!--     if (!col_setpoint %in% colnames(df_csv_filtered)) { -->
<!--       cat("[Warning] Cooling setpoint column not found:", col_setpoint, "\n") -->
<!--       cooling_setpoint_df <- data.frame(datetime = as.POSIXct(character()), value = numeric()) -->
<!--     } else { -->
<!--       cooling_setpoint_df <- df_csv_filtered %>% -->
<!--         select(datetime, value = all_of(col_setpoint)) %>% -->
<!--         drop_na() -->
<!--     } -->

<!--     param_combinations <- expand.grid(m_val = met_range, c_val = clo_range, stringsAsFactors = FALSE) -->

<!--     cat("  Starting parallel processing for", nrow(param_combinations), "Met/Clo combinations...\n") -->

<!--     # ------- progress var setting ------- -->
<!--     pb <- progress_bar$new( -->
<!--       format = "  Calculating [:bar] :percent (ETA: :eta)", -->
<!--       total = nrow(param_combinations), -->
<!--       clear = FALSE, -->
<!--       width = 80 -->
<!--     ) -->
<!--     progress <- function(n) pb$tick() -->
<!--     opts <- list(progress = progress) -->
<!--     # ------------------------------------ -->

<!--     # parallel loop calculation -->
<!--     parallel_results_list <- foreach( -->
<!--       i = 1:nrow(param_combinations), -->
<!--       .combine = "list", -->
<!--       .multicombine = TRUE, -->
<!--       .packages = c("reticulate", "dplyr", "tidyr"), -->
<!--       .export = c("df_csv_filtered", "room_names", "vr_values", "PYTHON_FUNCTION_STRING", "param_combinations"), -->
<!--       .errorhandling = "pass", -->
<!--       .options.snow = opts # progress bar -->
<!--     ) %dopar% { -->

<!--       tryCatch({ -->
<!--         if (!reticulate::py_has_attr(reticulate::py, "vectorized_pmv_all")) { -->
<!--           reticulate::py_run_string(PYTHON_FUNCTION_STRING) -->
<!--         } -->
<!--         m_val <- param_combinations$m_val[i] -->
<!--         c_val <- param_combinations$c_val[i] -->
<!--         param_label <- paste0("met_", sprintf("%.1f", m_val), "_clo_", sprintf("%.2f", c_val)) -->
<!--         current_param_room_results <- list() -->

<!--         for (room in room_names) { -->
<!--           col_temp <- paste0(room, ":Zone Mean Air Temperature [C](TimeStep)") -->
<!--           col_rad <- paste0(room, ":Zone Mean Radiant Temperature [C](TimeStep)") -->
<!--           col_hum <- paste0(room, ":Zone Air Relative Humidity [%](TimeStep)") -->
<!--           required_cols <- c("datetime", col_temp, col_rad, col_hum) -->

<!--           if (!all(required_cols %in% colnames(df_csv_filtered))) next -->

<!--           df_room <- df_csv_filtered %>% -->
<!--             select(all_of(required_cols)) %>% -->
<!--             transmute( -->
<!--               datetime = datetime, temperature = .data[[col_temp]], -->
<!--               radiant = .data[[col_rad]], humidity = .data[[col_hum]] -->
<!--             ) %>% -->
<!--             drop_na() -->

<!--           if (nrow(df_room) == 0) next -->

<!--           pmv_matrix_result <- py$vectorized_pmv_all( -->
<!--             df_room$temperature, df_room$radiant, df_room$humidity, vr_values, m_val, c_val -->
<!--           ) -->

<!--           if (!is.matrix(pmv_matrix_result)) stop("Python function did not return a matrix.") -->

<!--           pmv_df <- data.frame(datetime = df_room$datetime) -->
<!--           for (j_idx in seq_along(vr_values)) { -->
<!--             pmv_df[[paste0("PMV_vr_", sprintf("%.2f", vr_values[j_idx]))]] <- pmv_matrix_result[, j_idx] -->
<!--           } -->
<!--           current_param_room_results[[room]] <- pmv_df -->
<!--         } -->

<!--         list(status = "success", param_label = param_label, results = current_param_room_results) -->
<!--       }, error = function(e) { -->
<!--         list( -->
<!--           status = "error", -->
<!--           param_label = paste0("met_", param_combinations$m_val[i], "_clo_", param_combinations$c_val[i]), -->
<!--           error_message = as.character(e$message) -->
<!--         ) -->
<!--       }) -->
<!--     } -->

<!--     # merging results -->
<!--     all_pmv_data_for_case <- list() -->
<!--     error_list <- list() -->
<!--     for (res_item in parallel_results_list) { -->
<!--       if (!is.null(res_item$status) && res_item$status == "success") { -->
<!--         all_pmv_data_for_case[[res_item$param_label]] <- res_item$results -->
<!--       } else if (!is.null(res_item$status) && res_item$status == "error") { -->
<!--         error_list[[res_item$param_label]] <- res_item$error_message -->
<!--       } -->
<!--     } -->
<!--     if (length(error_list) > 0) { -->
<!--       cat("\n--- ERRORS OCCURRED DURING PARALLEL PROCESSING ---\n") -->
<!--       for (param_label in names(error_list)) { -->
<!--         cat(" Parameters:", param_label, "\n  * Root Cause Error:", error_list[[param_label]], "\n") -->
<!--       } -->
<!--       cat("---------------------------------------------------\n") -->
<!--     } -->

<!--     # save results -->
<!--     save_dir <- file.path("R.Data", country_name) -->
<!--     if (!dir.exists(save_dir)) dir.create(save_dir, recursive = TRUE) -->

<!--     save(all_pmv_data_for_case, cooling_setpoint_df, -->
<!--          file = file.path(save_dir, paste0("PMV_result_", case_label, ".RData")), compress = "xz") -->

<!--     all_case_results[[case_label]] <- list(PMV = all_pmv_data_for_case, Setpoint = cooling_setpoint_df) -->

<!--     case_end_time <- Sys.time() -->
<!--     cat("[Finished Case]:", case_label, "Total elapsed time:", round(difftime(case_end_time, case_start_time, units = "secs"), 2), "seconds\n\n") -->
<!--   } -->

<!--   return(all_case_results) -->
<!-- } -->
<!-- # ---- End ---- -->


<!-- # ======  Execute Functions ====== -->

<!-- ### For one city ### -->

<!-- # --- 1. Setup parallel clusters --- -->
<!-- # set num of core, as PC core-1, to avoid heavy operation -->
<!-- num_cores <- detectCores() - 1 -->
<!-- if (num_cores < 1) num_cores <- 1 -->
<!-- # register doSNOW, enabling progress bar -->
<!-- cl <- makeCluster(num_cores) -->
<!-- registerDoSNOW(cl) -->
<!-- cat(paste("Parallel backend registered with", num_cores, "cores.\n\n")) -->

<!-- # --- 2. Analysis --- -->
<!-- # Test case, max_outdoor_range=27:32 in SG -->
<!-- results_test <- analyze_nv_from_csv_multiroom_parallel( -->
<!--   country_name = "Singapore", -->
<!--   max_outdoor_range = 27:32 -->
<!-- ) -->
<!-- # --- 3. Stop clusters --- -->
<!-- stopCluster(cl) -->
<!-- cat("\nParallel backend stopped.\n") -->
<!-- # --- 4. Check results --- -->
<!-- if (!is.null(results_test)) { -->
<!--   cat("Analysis completed successfully.\n") -->
<!-- } else { -->
<!--   cat("An error occurred during the analysis.\n") -->
<!-- } -->

<!-- ### For multiple cities ### -->

<!-- # --- 0. Setup parallel clusters --- -->
<!-- # set num of core, as PC core-1, to avoid heavy operation -->
<!-- num_cores <- detectCores() - 1 -->
<!-- if (num_cores < 1) num_cores <- 1 -->
<!-- # register doSNOW, enabling progress bar -->
<!-- cl <- makeCluster(num_cores) -->
<!-- registerDoSNOW(cl) -->
<!-- cat(paste("Parallel backend registered with", num_cores, "cores.\n\n")) -->

<!-- # ---1. get city name vector --- -->
<!-- all_cities <- names(epw_dict) -->
<!-- cities_to_run <- all_cities[1:20] -->

<!-- # ---2. loop analysis --- -->
<!-- total_start_time <- Sys.time() -->

<!-- cat("===== STARTING BATCH ANALYSIS FOR MULTIPLE CITIES =====\n") -->
<!-- cat("Target cities:", paste(cities_to_run, collapse = ", "), "\n\n") -->

<!-- # try...finally, let clusters stop when error occurs during calculation -->
<!-- try({ -->
<!--   # loop cities -->
<!--   for (city in cities_to_run) { -->
<!--     cat(paste0("---------- Processing city: ", city, " ----------\n")) -->

<!--     # analysis -->
<!--     analyze_nv_from_csv_multiroom_parallel( -->
<!--       country_name = city, -->
<!--       max_outdoor_range = 27:32 -->
<!--     ) -->

<!--     cat(paste0("---------- Finished city: ", city, " ----------\n\n")) -->
<!--   } -->
<!-- }) -->
<!-- finally({ -->
<!--   # ---  stop clusters  --- -->
<!--   stopCluster(cl) -->
<!--   cat("\nParallel backend stopped.\n") -->

<!--   total_end_time <- Sys.time() -->
<!--   total_duration <- difftime(total_end_time, total_start_time) -->

<!--   cat("===== BATCH ANALYSIS COMPLETED =====\n") -->
<!--   cat("Total execution time:", round(total_duration, 2), units(total_duration), "\n") -->
<!-- }) -->
<!-- # ---- End ---- -->

```{r}
# PMV for multiple clo, MET setting 
```

## New loop based on city*temp cases, since each case is enough heavy to load functions

analyze_nv_from_csv_case <- function(country_name, max_outdoor,
                                     vr_values = c(0.1, 0.4, 0.8, 1.2, 1.6, 2.0),
                                     met_range = seq(0.8, 1.8, by = 0.1),
                                     clo_range = seq(0.3, 0.5, by = 0.04),
                                     base_path = path.expand("~/localdir/analysis/data/idf/12.cals"),
                                     room_names = NULL,
                                     python_script = NULL, # ここでスクリプトを渡す
                                     compress = "gzip") {
  
  # 1. 各コアでのPython初期化の徹底
  if (!reticulate::py_has_attr(reticulate::py, "vectorized_pmv_all")) {
    if (!is.null(python_script)) {
      reticulate::py_run_string(python_script)
    } else {
      return(list(status="error", reason="python_script_missing"))
    }
  }

  if (is.null(room_names)) {
    room_names <- c(
      "LIVING_UNIT1_FRONTROW_BOTTOMFLOOR","LIVING_UNIT2_FRONTROW_BOTTOMFLOOR","LIVING_UNIT3_FRONTROW_BOTTOMFLOOR",
      "LIVING_UNIT1_BACKROW_BOTTOMFLOOR","LIVING_UNIT2_BACKROW_BOTTOMFLOOR","LIVING_UNIT3_BACKROW_BOTTOMFLOOR",
      "LIVING_UNIT1_FRONTROW_MIDDLEFLOOR","LIVING_UNIT2_FRONTROW_MIDDLEFLOOR","LIVING_UNIT3_FRONTROW_MIDDLEFLOOR",
      "LIVING_UNIT1_BACKROW_MIDDLEFLOOR","LIVING_UNIT2_BACKROW_MIDDLEFLOOR","LIVING_UNIT3_BACKROW_MIDDLEFLOOR",
      "LIVING_UNIT3_BACKROW_TOPFLOOR","LIVING_UNIT3_FRONTROW_TOPFLOOR","LIVING_UNIT1_FRONTROW_TOPFLOOR",
      "LIVING_UNIT2_BACKROW_TOPFLOOR","LIVING_UNIT2_FRONTROW_TOPFLOOR","LIVING_UNIT1_BACKROW_TOPFLOOR"
    )
  }

  case_label <- paste0("MaxOutdoor_", max_outdoor)
  path_cal <- file.path(base_path, country_name, case_label)
  csv_path <- file.path(path_cal, "model_updated.csv")
  
  if (!file.exists(csv_path)) return(list(status="skip", reason="csv_not_found", country=country_name, case=case_label))

  # fread & フィルタリング
  df_csv_original <- data.table::fread(csv_path, check.names = FALSE, data.table = FALSE)
  if (nrow(df_csv_original) == 0) return(list(status="skip", reason="csv_empty", country=country_name, case=case_label))

  colnames(df_csv_original)[1] <- "datetime"
  df_csv_original <- df_csv_original[-c(1:288), ]

  # 日付パースの安全策
  df_csv_original$datetime <- as.POSIXct(gsub("  ", " ", df_csv_original$datetime), format="%m/%d %H:%M:%S")
  df_csv_filtered <- df_csv_original[!is.na(df_csv_original$datetime) & format(df_csv_original$datetime, "%M") == "00", ]
  
  if (nrow(df_csv_filtered) == 0) return(list(status="skip", reason="no_hourly_data", country=country_name, case=case_label))

  # PMV計算ループ (ここは既存ロジックを維持)
  param_combinations <- expand.grid(m_val=met_range, c_val=clo_range, stringsAsFactors=FALSE)
  all_pmv_data_for_case <- list()
  
  for (i in seq_len(nrow(param_combinations))) {
    m_val <- param_combinations$m_val[i]
    c_val <- param_combinations$c_val[i]
    param_label <- paste0("met_", sprintf("%.1f", m_val), "_clo_", sprintf("%.2f", c_val))
    current_param_room_results <- list()

    for (room in room_names) {
      col_temp <- paste0(room, ":Zone Mean Air Temperature [C](TimeStep)")
      col_rad  <- paste0(room, ":Zone Mean Radiant Temperature [C](TimeStep)")
      col_hum  <- paste0(room, ":Zone Air Relative Humidity [%](TimeStep)")
      
      if (!(col_temp %in% colnames(df_csv_filtered) && col_rad %in% colnames(df_csv_filtered) && col_hum %in% colnames(df_csv_filtered))) next

      df_room <- df_csv_filtered[, c("datetime", col_temp, col_rad, col_hum)]
      names(df_room) <- c("datetime","temperature","radiant","humidity")
      df_room <- df_room[complete.cases(df_room), ]
      if (nrow(df_room) == 0) next

      # Python呼び出し
      pmv_matrix_result <- reticulate::py$vectorized_pmv_all(
        df_room$temperature, df_room$radiant, df_room$humidity, vr_values, m_val, c_val
      )

      pmv_df <- data.frame(datetime=df_room$datetime)
      for (j_idx in seq_along(vr_values)) {
        pmv_df[[paste0("PMV_vr_", sprintf("%.2f", vr_values[j_idx]))]] <- pmv_matrix_result[, j_idx]
      }
      current_param_room_results[[room]] <- pmv_df
    }
    all_pmv_data_for_case[[param_label]] <- current_param_room_results
  }
  
  # analyze_nv_from_csv_case 関数内の save(...) の直前に追加
  cat(sprintf("\n[CHECK] Finished: %s - %s at %s\n", country_name, case_label, Sys.time()), 
    file = "progress_log.txt", append = TRUE)
  
  # 保存処理
  save_dir <- file.path("R.Data", country_name)
  if (!dir.exists(save_dir)) dir.create(save_dir, recursive = TRUE)
  save_path <- file.path(save_dir, paste0("PMV_result_", case_label, ".RData"))
  
  # Setpoint抽出
  col_setpoint <- "LIVING_UNIT1_FRONTROW_BOTTOMFLOOR:Zone Thermostat Cooling Setpoint Temperature [C](TimeStep)"
  cooling_setpoint_df <- if (col_setpoint %in% colnames(df_csv_filtered)) {
    tmp <- df_csv_filtered[, c("datetime", col_setpoint)]
    names(tmp)[2] <- "value"
    tmp[!is.na(tmp$value), ]
  } else {
    data.frame(datetime=as.POSIXct(character()), value=numeric())
  }

  save(all_pmv_data_for_case, cooling_setpoint_df, file = save_path, compress = compress)

  return(list(status="done", country=country_name, case=case_label, out=save_path))
}

# --- 実行セクション ---
# クラスター設定
<!-- num_cores <- parallel::detectCores() - 1 -->
# 1. クラスターのセットアップ（10コア推奨）
num_cores <- 12
cl <- makeCluster(num_cores)
registerDoSNOW(cl)

# 2. 関数と変数の配布
clusterExport(cl, c("PYTHON_FUNCTION_STRING", "analyze_nv_from_csv_case"))

# 3. タスクの定義
cities_to_run <- names(epw_dict)[21]
max_range <- 27:32
tasks <- expand.grid(city=cities_to_run, max_outdoor=max_range, stringsAsFactors=FALSE)

# 4. プログレスバーの定義 (ここでエラーが出ないように確実に作成)
pb <- txtProgressBar(max = nrow(tasks), style = 3)
progress <- function(n) setTxtProgressBar(pb, n)
opts <- list(progress = progress)

# 5. 実行
results <- foreach(ii = seq_len(nrow(tasks)),
                   .packages = c("data.table", "reticulate"),
                   .options.snow = opts,             # ここで opts を使用
                   .errorhandling = "pass") %dopar% {
  
  analyze_nv_from_csv_case(
    country_name = tasks$city[ii],
    max_outdoor = tasks$max_outdoor[ii],
    python_script = PYTHON_FUNCTION_STRING
  )
}

# 6. 後片付け
close(pb)
stopCluster(cl)

```{r}
# Loading multiple PMV data for clo, met combination
```

# 1. Load and data check, set path and parameters
# -----------------------------------
# project base path
base_path <- here::here() 

# check target city
city_name <- "Freetown"

# max outdoor temp range
temp_range <- 27:32

# 2. main loop
# -----------------------------------

# loop for max temp
for (temp in temp_range) {
  
  # set path for target R.Data file
  file_name <- paste0("PMV_result_MaxOutdoor_", temp, ".RData")
  file_path <- file.path(base_path, "R.Data", city_name, file_name)
  
  # check if the file exists
  if (!file.exists(file_path)) {
    warning(paste("no file detected:", file_path))
    next
  }
  
  # ---- show file contents ----
  cat("\n==========================================================\n")
  cat("📂 Checking:", file_name, "\n")
  cat("==========================================================\n\n")
  
  # temporaly loading
  temp_env <- new.env()
  load(file_path, envir = temp_env)
  
  # (1): get source list object 
  # check if this object exists
  if (exists("all_pmv_data_for_case", envir = temp_env)) {
    main_list <- get("all_pmv_data_for_case", envir = temp_env)
  } else {
    warning(paste("object 'all_pmv_data_for_case' not found:", file_name))
    next # skip this file, go to next file
  }
  
  # (2):loop for contents in the list (MET, CLO)
  # names(main_list), to get elements（met_0.8_clo_0.30 etc）
  for (element_name in names(main_list)) {
    
    # ---- show object information ----
    cat("-------------------------------------\n")
    cat("⦿ source list: all_pmv_data_for_case\n")
    cat("⦿ element", element_name, "\n")
    
    # (3): get element by name from list
    element_data <- main_list[[element_name]]
    
    # show contents of elements
    str(element_data) 
  }
}
